\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\documentclass{article}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{\textbf{Atharva Keshre}  \\}
\normalsize  Boston, MA  $\mid$ (617) 735-7893 $\mid$ \href{mailto:keshre.a@northeastern.edu}{Email} $\mid$ \href{https://www.linkedin.com/in/atharva-keshre}{LinkedIn} $\mid$  \href{https://github.com/AtharvaKeshre}{Github} $\mid$  \href{https://atharvakeshre08.wixsite.com/website}{Website}  \\
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Information Systems} \hfill \textbf{Sept 2023 - Present } \\
Northeastern University,Boston, MA {GPA: 3.686}\\
Courses: Application Engineering, Design, Web Design, User Experience, Data Management, Database Design\\\\
\textbf{Bachelor of Technology in Information Technology} \hfill \textbf{Aug 2016 - Aug 2020 } \\
Acropolis Institute of Technology and Research, India {GPA: 3.0} \\
Courses: Object Oriented Programming, Data Structures, Operating Systems, Analysis and Design of Algorithms.\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}: Python, C++, Java, SQL, PL/SQL, JavaScript, TypeScript, Go, Vue, HTML, XML, CSS, R \\
\textbf{Frontend Technologies}: React.js, Next.js, Angular, Redux, Vue.js, Tailwind CSS \\
\textbf{Backend Technologies}: Node.js, Express.js, Spring Boot, Hibernate, Microservices, Rest API \\
\textbf{Databases and Cloud}: PostgreSQL, MongoDB, MySQL, SQLite, AWS (EC2, S3, Lambda), Google Cloud Platform, Firebase \\
\textbf{Dev Tools and Operations}: Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes \\
\textbf{Testing and APIs}: Jest, Mocha, Cypress, RESTful Services, GraphQL, Apollo GraphQL, Postman, Swagger \\
\textbf{Additional Skills}: Responsive Web Design, Web Accessibility, Server-Side Rendering (SSR), WebSockets, OAuth, JWT.\\




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{\textit{Full Stack Developer} $\mid$ Zensar Technologies Pvt. Ltd.}  \hfill \textbf{Jan 2022 – July 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
   \item Led a 7-person team in developing a dynamic MERN stack application, achieving a 30\% increase in development efficiency by creating reusable components and modular server-side functionalities.
   \item Transformed the application into a Progressive Web App (PWA), resulting in a 25\% increase in user engagement and a 15\% improvement. Implemented MongoDB-backed RESTful APIs to enhance frontend-backend communication efficiency by 40\%.
   \item Deployed serverless backends using AWS Lambda, seamlessly integrated with React frontends, leading to a 10\% reduction in server costs and improved scalability.
   \item Automated CI/CD pipelines with GitHub Actions and Docker, improving development speed by 35\% and reducing deployment time by 25\%, optimizing the overall productivity and release cycles.
\end{itemize}

\vspace{1mm}

\noindent \textbf{Junior Full Stack Developer $\mid$ Zensar Technologies Pvt. Ltd.} \hfill \textbf{July 2020 –Jan 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
     \item Spearheaded frontend development within an Agile (Scrum) team, leveraging the powerful capabilities of React and Redux frameworks. This approach enabled the team to deliver projects 20\% faster while maintaining high code quality.
    \item Developed a comprehensive React component library with streamlined templates, which increased development speed by 25\% and significantly enhanced component reusability across multiple projects.
    \item Utilized React's efficient data flow architecture to design lightweight, high-performance web applications, which resulted in a 30\% improvement in load times and ensured that the applications were highly scalable and responsive to user interactions.
    \item Implemented and managed an extensive suite of unit tests and integration testing for server-side applications using Jest and Cypress. This rigorous testing framework enhanced overall code stability and reduced the incidence of bugs by 40\%.\\
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\textbf{\textbf{UNIOne } $\mid$ Tailored Solutions, Seamless Management} $\mid$ \textbf{Java, MySQL} \hfill {\textbf{\textbf{Sept 2023 – Dec 2023} }}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Designed a Java Swing application integrated with MySQL database, encompassing modules such as cafeteria, library, employer portal, and IT support optimize resource allocation, resulting in a 20\% efficiency in administrative tasks.
\item Engineered an innovative car rental app utilizing MERN stack, Redux, Mongoose, Material UI, and Tailwind CSS. Employed matrices for data analysis, optimizing user experience and achieving a 30\% increase in booking efficiency.

\end{itemize}
\textbf{\textbf{DriveEz } $\mid$ Auto Rental Application} $\mid$ \textbf{MERN Stack, JavaScript, HTML, CSS}  \hfill \textbf{\textbf{Sept 2023 – Dec 2023}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Developed a MERN stack car rental application with Google Maps integration and multilingual support, leading to a 30\% increase in the user base.
    \item Coordinated backend and frontend integration using RESTful APIs, improving system efficiency by 25\%.

\end{itemize}
\textbf{\textbf{Fleet Rental Database Management System } $\mid$ \textbf{MySQL, SQL, T-SQL, React, Express} } \hfill \textbf{\textbf{Jan 2024 – April 2024} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Established a Fleet Rental Database System using MySQL to manage 500+ vehicles, 1,000+ customers, and 2,000+ transactions. Employed Node.js, Express.js, Axios, and React to create an intuitive user interface and facilitate CRUD operations.
    \item Leveraged MySQL's advanced features, including user-defined functions, stored procedures, and triggers, to enforce business rules, automate tasks, and enhance data integrity, resulting in a 20\% reduction in Car rental Apps.
\end{itemize}
\textbf{\textbf{Handwritten Text Recognition Tool (HTR) } $\mid$ \textbf{Python, Flask, ML, JavaScript} } \hfill \textbf{\textbf{May 2020 – Aug 2020} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Developed a web-based application with Python 3, HTML 5, CSS 3, Bootstrap, and Flask to convert machine-printed or handwritten text from images into digital format, enhancing accuracy by 25\% in text recognition tasks.
    \item Integrated Tesseract OCR, Machine Learning (ML), and Deep Learning (DL) technologies to boost the accuracy, performance evaluation, achieving a 30\% increase in text recognition accuracy through algorithmic optimization.
\end{itemize}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
