\documentclass{article}

\usepackage[top=0.2in, bottom=0.2in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\documentclass{article}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{\textbf{Atharva Keshre}  \\}
\normalsize  Boston, MA   $\mid$ (617) 735-7893 $\mid$ \href{mailto:keshre.a@northeastern.edu}{Email} $\mid$ \href{https://www.linkedin.com/in/atharva-keshre}{LinkedIn} $\mid$  \href{https://github.com/AtharvaKeshre}{Github} $\mid$  \href{https://atharvakeshre08.wixsite.com/website}{Website}  \\
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Information Systems} \hfill \textbf{Sept 2023 - Present } \\
Northeastern University,Boston, MA {GPA: 3.686}\\
Courses: Application Engineering, Design, Web Design, User Experience, Data Management, Database Design\\\\
\textbf{Bachelor of Technology in Information Technology} \hfill \textbf{Aug 2016 - Aug 2020 } \\
Acropolis Institute of Technology and Research, India {GPA: 3.0} \\
Courses: Object Oriented Programming, Data Structures, Operating Systems, Analysis and Design of Algorithms.

\vspace{2mm}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}: Python, C++, SQL, PL/SQL, JavaScript, TypeScript, Go, Vue, HTML, XML, CSS, R \\
\textbf{Backend Technologies}: Node.js, Express.js, Spring Boot, Hibernate, Microservices, Rest API, GraphQL, Apollo GraphQL \\
\textbf{Databases and Cloud}: PostgreSQL, MongoDB, MySQL, SQLite, AWS (EC2, S3, Lambda), Google Cloud Platform, Firebase \\
\textbf{Dev Tools and Operations}: Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes \\
\textbf{Testing and APIs}: Jest, Mocha, Cypress, RESTful Services, GraphQL, Apollo GraphQL, Postman, Swagger \\
\textbf{Additional Skills}: Server-Side Rendering (SSR), WebSockets, OAuth, JWT, Web Accessibility.

\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{\textit{Back End Developer} $\mid$ Zensar Technologies Pvt. Ltd.} \hfill \textbf{Jan 2022 – July 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Led a 7-person team in developing a dynamic MERN stack application, focusing on creating modular server-side functionalities and reusable components, resulting in a 30\% increase in development efficiency.
\item Implemented MongoDB-backed RESTful APIs, enhancing frontend-backend communication efficiency by 40\%, improving data retrieval, and ensuring a seamless user experience.
\item Transformed the application into a Progressive Web App (PWA), resulting in a 25\% increase in user engagement and a 15\% improvement in mobile performance metrics.
\item Deployed serverless backends using AWS Lambda, seamlessly integrating with React frontends, reducing server costs by 10\% and improving scalability to handle increased user loads efficiently.
\item Automated CI/CD pipelines using GitHub Actions and Docker, significantly improving development speed by 35\% and reducing deployment time by 25\%, optimizing overall productivity and minimizing deployment-related issues.
\end{itemize}

\vspace{1mm}

\noindent \textbf{\textit{Junior Back End Developer} $\mid$ Zensar Technologies Pvt. Ltd.} \hfill \textbf{July 2020 – Jan 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Spearheaded backend development within an Agile (Scrum) team, leveraging the capabilities of Node.js and Express.js frameworks to deliver projects 20\% faster while maintaining high code quality.
\item Developed comprehensive server-side logic and API endpoints, which increased development speed by 25\% and ensured seamless data flow and communication.
\item Utilized MongoDB and SQL databases to design efficient data storage solutions, resulting in a 30\% improvement in query performance and application scalability.
\item Implemented and managed an extensive suite of unit tests and integration testing for server-side applications using Jest and Mocha. This rigorous testing framework enhanced overall code stability and reduced the incidence of bugs by 40\%.
\end{itemize}

\vspace{2mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\textbf{\textbf{UNIOne } $\mid$ Tailored Solutions, Seamless Management $\mid$ MySQL, Java Swing  } \hfill {\textbf{\textbf{Sept 2023 – Dec 2023} }}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
   \item Designed and implemented backend functionality for a university management system using Java Swing and MySQL, improving operational efficiency by 40\%.
    \item Developed modules for cafeteria, library, employer portal, and IT support, ensuring seamless university operations, leading to a 35\% reduction in manual processes.

\end{itemize}
\textbf{\textbf{DriveEz } $\mid$ Auto Rental Application $\mid$ JavaScript (Node.js, Express.js), MongoDB} \hfill \textbf{\textbf{Sept 2023 – Dec 2023}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Engineered backend services for a car rental app using the MERN stack, Redux, Mongoose, Material UI, and Tailwind, increasing backend performance by 50\% interactive map interface with personalized markers and internationalization (i18n), expanding the user base by 30\%.
    \item Orchestrated seamless integration between backend and frontend components through RESTful APIs, ensuring robust performance and dynamic data handling, achieving 25\% faster data retrieval.

\end{itemize}
\textbf{\textbf{Fleet Rental Database Management System $\mid$ JavaScript (Node.js), SQL (MySQL)}  } \hfill \textbf{\textbf{Jan 2024 – April 2024} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
   \item Established a Fleet Rental Database System using MySQL and SQL to manage vehicles, customers, rentals, and transactions, reducing data retrieval time by 45\%.
    \item Utilized MySQL's advanced features like user-defined functions, stored procedures, and triggers to enforce business rules and enhance data integrity, improving data accuracy by 40\%.


\end{itemize}
\textbf{\textbf{Handwritten Text Recognition Tool (HTR) }  $\mid$ \textbf{Python (Flask), HTML, CSS, JS} } \hfill \textbf{\textbf{May 2020 – Aug 2020} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Developed a web-based application using Python 3, Flask, HTML 5, CSS 3, JavaScript, and Bootstrap to convert machine-printed or handwritten text from images into machine-readable text, resulting in a 50\% reduction in manual data entry time.
    \item Integrated Tesseract OCR and machine learning algorithms to improve accuracy and efficiency in text recognition, reducing processing time by 50\%.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
