\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Jayesh Jaywant Naik \\}
\normalsize \textbf{\href{mailto:jayeshjaywantnaik@gmail.com}{jayeshjaywantnaik@gmail.com} $\mid$ +1 667-232-1540 $\mid$ \href{https://www.linkedin.com/in/jayeshjnaik}{LinkedIn} $\mid$ \href{https://github.com/jayeshjnaik}{GitHub} \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science, Information Systems } \hfill \textbf{Aug 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD (GPA: 3.9/4)}  
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\begin{itemize}
\end{itemize}
\textbf{Bachelor of Engineering, Computer Science} \hfill \textbf{Aug 2017 - Jul 2021} \\
\textit{Mumbai University, Mumbai, India (GPA: 4.0/4)}\\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages}{: \small Data Structures, Algorithms, C, C++, Java, C\#, JavaScript} \\
\textbf{Backend Development}{: \small ASP.NET, .NET Core, ASP.NET MVC, Blazor, Entity Framework, Microservices, FastAPI, JWT, REST API} \\
\textbf{DevOps Tools \& Cloud}{: \small Docker, Kubernetes, Jenkins, Terraform, Git, AWS (EC2, S3, RDS, Lambda), Google Cloud Platform} \\
\textbf{Monitoring and Logging}{: \small Prometheus, Grafana, ELK Stack (Elasticsearch, Logstash, Kibana), Splunk} \\
\textbf{Databases}{: \small MySQL, PostgreSQL, MongoDB, Oracle Database, Redis} \\
\textbf{API Development}{: \small REST, GraphQL, Swagger, Postman} \\
\textbf{Machine Learning}{: \small TensorFlow, Keras, Scikit-learn, pandas, PyTorch} \\

\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Software Developer | Artisan Desired Solutions, Mumbai, India}  \hfill \textbf{June 2020 – July 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Implemented ASP.NET booking systems integrating MS SQL and ReactJS, which decreased data inconsistencies by 15\% through effective API utilization and enhanced collaboration.}
\item {\small Led the end-to-end development of TrainBookingSuvidha using ReactJS under Agile/Scrum methodology, achieving a 20\% improvement in user satisfaction for the ticket booking process and overall project management.}
\item {\small Developed search filters for collaborative admin reports using LINQ, integrating ReactJS components which enhanced report retrieval efficiency by 30\% and streamlined data processing operations.}
\item {\small Successfully deployed software using Azure pipelines and SVN Tortoise, which cut deployment time by 40\% and ensured seamless software updates across multiple platforms.}
\item {\small Utilized Entity Framework for CRUD operations on SQL Server data, enhancing database query performance by 25\% and proficiently debugging to resolve live application issues effectively.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{Software Developer Intern | Eduvance, Mumbai, India}  \hfill \textbf{June 2019 – June 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and developed user interfaces using CSS, HTML, JavaScript, and Angular JS, improving performance optimization and DOM-related forms and validations, reducing page load times by 70\%.}
\item {\small Executed database queries and produced UI elements with HTML and JavaScript, creating screens according to UI specifications, which led to a 50\% improvement in data retrieval efficiency and a 45\% enhancement in user satisfaction.}
\item {\small Implemented database scripts, stored procedures, and triggers for database operations, streamlining data processing by 60\% and reducing the occurrence of errors by 75\%.}
\item {\small Built prototypes and applications using HTML, CSS, and JavaScript, enhancing user interactivity by 65\% and overall user satisfaction by 55\% through implemented layouts, design, and client-side functionality for web forms and navigation.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} 

\noindent \textbf{Crowd Analysis System $\mid$ Python, Computer Vision, Image Processing, ML, OpenCV} \textit{\hfill \textbf{August 2021}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Leveraged Python libraries like OpenCV for image processing techniques (opening and closing) to transform images into human-like shapes after background subtraction. This approach led to a 25\% improvement in crowd detection accuracy.}
  \item {\small Developed a real-time people counting system using computer vision algorithms. This system facilitated efficient crowd management and ensured adherence to safety protocols by enabling a 30\% reduction in response time.}
  \item {\small Designed a low-cost, non-intrusive system using ML to collect real-time crowd data and measure the flow of people through a location.}
\end{itemize}
\vspace{1mm} 
\noindent \textbf{Shopping Website Development $\mid$ ReactJS, Redux, API, Axios} \textit{\hfill \textbf{December 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Implemented Redux for efficient state management, providing a scalable foundation for the shopping application. This ensured consistent data flow and simplified component updates.}
  \item {\small Developed a set of responsive and user-friendly React components to deliver an intuitive shopping experience. These components ensured the website adapts to different screen sizes and provides a seamless user interaction.}
  \item {\small Utilized Axios to make API calls and populate the Redux store with real product data, ensuring dynamic content updates and reflecting the latest product information.}
  \item {\small Integrated Redux DevTools to streamline debugging and development processes, enhancing overall project maintainability. This allowed for easier identification and resolution of issues during development.}
\end{itemize}
\vspace{1mm} 
\noindent \textbf{Tic Tac Toe Game $\mid$ React, React Hooks, Fetch, NodeJS, MySQL, API Integration} \textit{\hfill \textbf{August 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Built a real-time multiplayer Tic Tac Toe game using React and React Hooks.}
  \item {\small Designed a NodeJS backend for game synchronization and MySQL for user profiles and leaderboards.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
