\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Rachna Malav \\}
\normalsize \textbf{\href{mailto:rachnamalav11@gmail.com}{rachnamalav11@gmail.com} $\mid$ +1 (509) 505-8621 $\mid$ \href{https://www.linkedin.com/in/rachna-malav/}{Linkedin} \\}
\rule{\textwidth}{1pt}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Bachelor of Science in Mathematics} \hfill \textbf{August 2019 - May 2023} \\
\textit{Whitworth University}\\
Minor: Computer Science (GPA: 3.65/4)\\
Relevant Coursework: Data Structures, Data Science, Database Management, Artificial Intelligence, Mathematical Statistics, Graph Theory \& Combinatorics, Linear Algebra, Abstract Algebra, Real Analysis, Discrete Math, Multivariable Calculus\\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}{: \small SQL, R, Python, C++, Java, JavaScript, HTML, CSS} \\
\textbf{Data Skills \& Cloud}{: \small Data Analysis, Data Cleaning, Data Modeling, Data Visualization, Regression Testing, Amazon Web Services} \\
\textbf{Statistical Analysis}{: \small t-test, linear regression, hypothesis testing, Probability} \\
\textbf{Visualization Tools}{: \small Tableau, AWS QuickSight, Power BI} \\
\textbf{Machine Learning}{: \small Pandas, NumPy, Matplotlib, Keras, TensorFlow} \\
\textbf{Databases \& Tools}{: \small MySQL, MongoDB, Redis, MS Excel, Google Sheets, MS Office Suite, VS Code, Project Management, Jira, GitHub} \\


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}}\\
\noindent \textbf{Junior Analytics Engineer | Vega Cloud Inc., Liberty Lake, WA} \hfill \textbf{July 2023 - Feb 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Collaborated with data engineers, analysts, and other stakeholders to understand data requirements/ETL process and translated them into technical solutions as per the client’s needs and feature requests.}
\item {\small Developed DBT/SQL data models, ensured data integrity and accuracy by curating data for analytics, and followed Agile methodologies to manage tasks in GitHub and Jira.}
\item {\small Optimized SQL queries and database performance to support efficient data retrieval and conducted data validations by analyzing data in MS Excel, which increased data accuracy by approximately 10\%.}
\item {\small Reported curated data for visualization by ingesting datasets in Amazon Redshift, created QuickSight analyses and published 50 dashboards integrated into Vega’s platform.}
\item {\small Conducted dynamic bi-weekly regression testing of QuickSight releases on Vega’s platform to ensure precision in data changes and visualizations for 135 client tenants.}
\item {\small Contributed to the creation of additional QuickSight dashboards with enhanced features and functionalities for Vega’s platform demo, which resulted in getting 15 new clients.}\\
\end{itemize}
\noindent \textbf{Human Resources Data Assistant | Whitworth University, Spokane, WA} \hfill \textbf{June 2022 - May 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Demonstrated exceptional attention to detail and discretion in securely handling confidential documents of 250+ employees and streamlined logistical operations to implement practices that resulted in a 20\% increase in data pipeline efficiency.}
\item {\small Performed tasks such as data entry, scanning, indexing, and updating employee records on SharePoint and provided unparalleled customer service by attentively assisting visitors with their inquiries and concerns, as well as professionally addressing incoming phone calls.}\\
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Accenture Data Analytics and Visualization Job Simulation (via Forage)} \textit{} \href{https://forage-uploads-prod.s3.amazonaws.com/completion-certificates/Accenture%20North%20America/hzmoNKtzvAzXsEqx8_Accenture%20North%20America_38x5Fxx8tiXq8TDND_1709953791876_completion_certificate.pdf}{\textcolor{Link}} 
\hfill \textbf{March 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Completed a simulation focused on advising a hypothetical social media client as a Data Analyst at Accenture.}
\item {\small Cleaned, modeled, and analyzed 7 datasets in Excel to uncover insights into content trends to inform strategic decisions.}
\item {\small Prepared a PowerPoint deck and video presentation to communicate key insights for the client and internal stakeholders.}\\
\end{itemize}
\noindent \textbf{Goldman Sachs Software Engineering Job Simulation (via Forage)} \textit{} \href{https://forage-uploads-prod.s3.amazonaws.com/completion-certificates/Goldman%20Sachs/NPdeQ43o8P9HJmJzg_Goldman%20Sachs_38x5Fxx8tiXq8TDND_1680767952709_completion_certificate.pdf}{\textcolor{Link}} 
\hfill \textbf{April 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Performed a job simulation as a Goldman Sachs Governance Analyst and assessed IT security to suggest improvements.}
\item {\small Identified that the company was using an outdated password hashing algorithm by cracking 100\% of the passwords from a leaked database using Hashcat.}
\item {\small Proposed actionable solutions to increase the company’s level of password protection such as enforcing a minimum password length of 12 characters and using a dedicated hashing algorithm.}\\
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{CERTIFICATIONS}} \\
\noindent \textbf{FinOps Certified Practitioner} \hfill \textbf{July 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Acquired comprehensive knowledge of the FinOps lifecycle and its Inform, Optimize, and Operate phases.}
\item {\small Demonstrated application of FinOps principles to drive increased business intelligence from cloud expenditure and developed proficiency in various cloud service providers such as AWS, Azure, and GCP.}\\
\end{itemize}
\noindent \textbf{Data Analytics on AWS (Amazon Web Services)} \hfill \textbf{April 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Achieved proficiency in utilizing cloud-based tools and services like S3, CloudTrail, and Athena for data analysis.}
\item {\small Attained mastery in building visualizations in AWS QuickSight for descriptive analytics.}
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}