\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\documentclass{article}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{\textbf{Atharva Keshre}  \\}
\normalsize  Boston, MA   $\mid$ (617) 735-7893 $\mid$ \href{mailto:keshre.a@northeastern.edu}{Gmail} $\mid$ \href{https://www.linkedin.com/in/atharva-keshre}{LinkedIn} $\mid$  \href{https://github.com/AtharvaKeshre}{Github} $\mid$  \href{https://atharvakeshre08.wixsite.com/website}{Website}  \\
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Information Systems} \hfill \textbf{Sept 2023 - Present } \\
Northeastern University,Boston, MA {GPA: 3.83}\\
Courses: Application Engineering \& amp; Design, Web Design \&amp; User Experience, Data Management \& amp; Database Design\\\\
\textbf{Bachelor of Technology in Information Science \& Engineering } \hfill \textbf{August 2014 - May 2018 } \\
Acropolis Institute of Technology and Research, India {GPA: 8.2} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}: Python, C++, Java, SQL, PL/SQL, JavaScript, TypeScript, Go, Vue, HTML, XML, CSS, R \\
\textbf{Frontend Technologies}: React.js, Next.js, Angular, Redux, Vue.js, Tailwind CSS \\
\textbf{Backend Technologies}: Node.js, Express.js, Spring Boot, Hibernate, Microservices, Rest API \\
\textbf{Databases and Cloud}: PostgreSQL, MongoDB, MySQL, SQLite, AWS (EC2, S3, Lambda), Google Cloud Platform, Firebase \\
\textbf{Dev Tools and Operations}: Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes \\
\textbf{Testing and APIs}: Jest, Mocha, Cypress, RESTful Services, GraphQL, Apollo GraphQL, Postman, Swagger \\
\textbf{Additional Skills}: Responsive Web Design, Web Accessibility, Server-Side Rendering (SSR), WebSockets, OAuth, JWT\\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Frontend Developer — Zensar Technologies Pvt. Ltd.}
\hfill \textbf{Jan 2022 – July}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
     \item Led frontend development efforts in a 7-person team for a MERN stack application, achieving a 25\% increase in user engagement through intuitive UI/UX enhancements.
    \item Implemented Domain-Driven Design (DDD) principles to ensure a scalable and maintainable frontend architecture, resulting in improved code quality and developer productivity.
    \item Transformed the application into a Progressive Web App (PWA), seamlessly integrating web and mobile features, driving a 25\% increase in user engagement and accessibility.
    \item Utilized AWS Lambda for serverless backend deployments, tightly integrated with React frontends, optimizing application performance and scalability.
\end{itemize}


\noindent \textbf{Junior Frontend Developer — Zensar Technologies Pvt. Ltd.} \hfill \textbf{July 2020 –Jan 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
      \item Spearheaded frontend development initiatives within an Agile (Scrum) team, leveraging JavaScript, React, and Redux frameworks, resulting in a 20\% improvement in development speed.
    \item Created a reusable React component library, reducing development time by 15\% and enhancing code maintainability across projects.
    \item Designed lightweight and high-performance web applications using React's efficient data flow architecture, ensuring optimal user experiences and scalability.
    \item Implemented comprehensive unit tests and integration testing using Jest and Cypress, improving code stability by 25\% and facilitating seamless feature integration.\\
\end{itemize}





\vspace{2mm}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\textbf{\textbf{UNIOne } $\mid$ Tailored Solutions, Seamless Management $\mid$ Java Swing, HTML, CSS, JavaScript} \hfill {\textbf{\textbf{Sept 2023 – Dec 2023} }}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
   \item Designed and developed frontend interfaces for a Java Swing application with MySQL backend, catering to university management needs such as cafeteria, library, employer portal, and IT support.
    \item Integrated an enterprise solution model into the application, allowing universities to customize features based on their specific requirements, enhancing user satisfaction and usability.

\end{itemize}
\textbf{\textbf{DriveEz } $\mid$ Auto Rental Application $\mid$ React.js, JavaScript, HTML, CSS} \hfill \textbf{\textbf{October 2022 – December 2023}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item EDeveloped a MERN stack car rental application integrating Redux, Mongoose, Material UI, and Tailwind, showcasing modern development practices.
    \item Utilized Google Maps API to create an interactive map interface with personalized markers and internationalization (i18n), expanding the user base by 30%.

\end{itemize}
\textbf{\textbf{Fleet Rental Database Management System $\mid$ React.js, JavaScript, HTML, CSS}  } \hfill \textbf{\textbf{Jan 2024 – April 2024} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
   \item Developed and maintained frontend features for a Fleet Rental Database System using MySQL, Node.js, Express.js, Axios, and React, enabling intuitive user interactions and CRUD operations.
    \item Leveraged MySQL's advanced features such as user-defined functions, stored procedures, and triggers to enforce business rules and enhance data integrity in the application.


\end{itemize}
\textbf{\textbf{Handwritten Text Recognition Tool (HTR) }  $\mid$ \textbf{HTML, CSS, JavaScript} } \hfill \textbf{\textbf{May 2020 – Aug 2020} }
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Collaborated in frontend development for a web-based application utilizing Python, Flask, HTML, CSS, Bootstrap, and JavaScript to convert machine-printed or handwritten text from images into machine-readable format.
    \item Utilized Tesseract OCR, Machine Learning (ML), and Deep Learning (DL) techniques to improve accuracy and efficiency of text recognition within the application, enhancing overall usability.
\end{itemize}







%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
