\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Simarpreet Saggu \\}
\normalsize Toronto, Ontario $\mid$ {\href{mailto:saggusimarpreet3@gmail.com}{Email}}$\mid$ +1437-974-6363 $\mid$ \href{https://www.linkedin.com/in/simarpreetsaggu/}{Linkedin} $\mid$ \href{}{}   \\
\hrulefill
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Ontario Graduate Certificate $\mid$ Public Relations Management} \hfill \textbf{January 2023 - September 2023} \\
\textbf{Ontario Graduate Certificate $\mid$ Human Resources Management} \hfill \textbf{January 2022 -  September 2022} \\
\textit{York University $\mid$ Toronto, Ontario}\\ 


\noindent\textbf{Bachelor of Commerce $\mid$ First Division} \hfill \textbf{August 2017 -   October 2020} \\
\textit{Sri Guru Tegh Bahadur Khalsa College, University of Delhi $\mid$ India} 
\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\noindent\textbf{HR Management:} HRIS (Human Resource Information System) Software, Payroll Systems, Administration Software.

\noindent\textbf{Employee Relations:} Conflict Resolution Tools, Employee Feedback Platforms, Performance Management Systems.

\noindent\textbf{Coaching and Leadership Development:} Talent Management Systems, 360-Degree Feedback, CoachAccountable.

\noindent\textbf{Analytical Thinking:} Analytics Tools (Visier, ADP DataCloud), Excel and Data Analysis Software, Tableau, Power BI.

\noindent\textbf{HR Shared Services:} Case Management Systems, ServiceNow HR Service Delivery, Knowledge Management Tools.

\noindent \textbf{HR Management Systems:} Workday, SAP SuccessFactors, Oracle HCM Cloud, ADP Workforce Now.

\noindent\textbf{Problem-Solving:} Root Cause Analysis Tools, Decision-Making Software( Decision Lens) Asana, Trello.

\noindent \textbf{Data Analysis:} SQL, Python (for data analysis and visualization), R (for statistical analysis).

\noindent \textbf{General Tools:} Microsoft Excel (Advanced level).

\noindent \textbf{Lean Mindset:} Lean Six Sigma Tools, Minitab, Process Street, UiPath.
\vspace{2mm} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} 

\noindent \textbf{Sales Executive \& Head Cashier, Browns $\mid$ Toronto, Ontario} \hfill \textbf{September 2022 – Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Led product training sessions using HRM expertise, boosting customer satisfaction by 15\%, as shown by positive Google reviews.}
\item {\small Maintained accurate cash and inventory records, achieving a 98\% accuracy rate in reconciliation and cash management.}
\item {\small Implemented cash handling processes, reducing transaction time by 10\% and consistently achieving 120\% of monthly sales targets.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{Team Lead, Front Street Solutions $\mid$ Toronto, Ontario} \hfill \textbf{April 2022 – September 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Managed a team of 15 door-to-door fundraisers, providing coaching and feedback, which increased team performance by 20\%.}
\item {\small Conducted training sessions for new members, improving onboarding and retention rates by 25\%.}
\item {\small Addressed fundraising challenges, reducing objections and rejections by 30\% through effective situational training.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{HR Coordinator, Four Falcon Management Services Pvt Ltd $\mid$ Delhi, India} \hfill \textbf{July 2021 – April 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Coordinated HR activities for a team of 10, enhancing performance by 18\% through regular feedback and coaching.}
\item {\small Conducted onboarding and skill development sessions for new hires, improving employee retention by 30\%.}
\item {\small Resolved HR issues, reducing conflict resolution time by 20\% and improving overall employee satisfaction.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{Assurance Associate, Ernst \& Young (EY) $\mid$ Delhi, India} \hfill \textbf{October 2020 – June 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Conducted financial statement audits for high-profile clients, such as COCA-COLA, contributing to a 98\% client satisfaction rate.}
\item {\small Organized team meetings and building exercises, improving team collaboration and productivity by 15\%.}
\item {\small Prepared and reviewed audit worksheets, assisting in planning and executing procedures, reducing risk assessment errors by 10\%.}
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Community Service}} \\
\noindent \textbf{Senior Correspondent, The Business Café $\mid$ Delhi, India} \hfill \textbf{August 2019 – August 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Researched and wrote 50+ articles for the college magazine, increasing reader engagement by 20\% through informative content.}
\item {\small Conducted 30+ interviews with faculty, staff, and students, enhancing the quality of content and credibility of articles.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{Project Head, ENACTUS, SGTB Khalsa College $\mid$ Delhi, India} \hfill \textbf{August 2018 – August 2019}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Led Project Aaghaz, promoting crochet products and generating INR 25k in sales, benefiting 10 Afghan refugee families.}
\item {\small Developed marketing strategies and new product designs, increasing sales by 30\% through innovative approaches.}
\item {\small Directed a team of 20 members to work with refugee families, enhancing their business sustainability by 40\%.}
\end{itemize}

\vspace{1mm}

\noindent \textbf{Joint Secretary, Ankur- Street Theatre Society, Khalsa College $\mid$ Delhi, India} \hfill \textbf{August 2017 – August 2018}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Managed a team of 35 members, addressing attendance and grievances, ensuring 95\% participation and team satisfaction.}
\item {\small Coordinated and performed 100+ street plays, increasing public awareness on social issues by 25\% across Delhi.}
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{Certifications}} \\
\noindent \textbf{EY BETTER ME – WELL BEING BRONZE} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Earner of this badge is an emerging leader who wants to develop their transformational leadership skills. }
\end{itemize}

\vspace{2mm}

\noindent \textbf{\underline{References}} \\
\noindent \textbf{Alaadine Eter} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Manager, Browns :- 647-860-5536 }
\item {Valay Vaidya, PWC (EX- EY) :- 647-996-3355}
\end{itemize}


\end{document}
