\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Arunima Sharma \\}
\normalsize \textbf{\href{mailto:arunima4work@gmail.com}{arunima4work@gmail.com} $\mid$ +1 647 561 0963 $\mid$ \href{https://www.linkedin.com/in/arunima13}{LinkedIn}}
$\mid$ \normalsize \textbf{Toranto, Canada \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science, Project Management} \hfill \textbf{Sept 2021 - Apr 2023} \\
\textit{Northeastern University, Toronto, Canada GPA: 3.84}  
\vspace{2mm}
\end{itemize}
\textbf{Bachelor of Technology, Engineering} \hfill \textbf{Aug 2005 - Aug 2009} \\
\textit{Satyabhama University, India GPA: 3.5}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Technical Skills:}{: \small Atlassian Jira, Confluence, Rally, Azure DevOps, SharePoint, MS Project, Service Now, Slack, Power BI, Tableau, R, SQL, QlikView, Lucidchart, Miro, MS Office, Visio, Primavera, Informatica} \\
\textbf{Professional Skills:}{: \small Team Development, Interpersonal Skills, Customer Relationship Management (CRM), Creative Problem Solving, Leadership, Project Management, Business Analytics, Problem Solving, Servant Leadership, Scaled Agile Framework, Agile Methodologies} \\
\textbf{Management Skills:}{: \small Backlog Management, Sprint Planning, Stakeholder Communication, Continuous Improvement, Conflict Resolution, Agile Metrics, Team Scheduling, Change Management, Risk Management.}
\end{itemize}
\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Business Analyst | NEU Finance Portal – Northeastern’s Experiential Learning}  \hfill \textbf{Dec2022 - Apr2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Collaborated with over 50 students and finance team members to identify and address limitations within the complex payment systems. This effort resulted in a 30\% reduction in processing time and a 20\% increase in user satisfaction.}
\item {\small Developed and managed a Jira dashboard to track team progress, creating and maintaining over 20 delivery reports. This improved project transparency, leading to a 15\% boost in team efficiency.}
\item {\small Communicated changes, proposals, and improvements in value increments to stakeholders during 10+ meetings. This resulted in a 25\% increase in stakeholder satisfaction and a 10\% improvement in project alignment.}
\item {\small Created data visualizations and forecasts to simplify system complexity for over 5,000 students and finance staff. This led to a 40\% decrease in user-reported issues and a 15\% improvement in system usability.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst | Maine Shellfish Developers – Client Initiative at Northeastern}  \hfill \textbf{Jan2022 - Jul2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Facilitated Joint Requirement Planning (JRP) sessions with 10+ Business User Groups and conducted Joint Application Development (JAD) sessions with IT Groups. Managed conflict resolution within the project team, resulting in a 15\% reduction in project delays.}
\item {\small Assessed business and technical requirements and developed an actionable plan. Successfully implemented objectives and evaluated results, achieving a 25\% increase in project efficiency.}
\item {\small Created detailed Business Requirements including user stories, traceability matrices, and dashboards using Power BI. These efforts improved requirement traceability by 30\%.}
\item {\small Drafted final sponsor presentations and sprint reviews, effectively communicating goals, strategies, and anticipated outcomes to company sponsors. This increased sponsor approval rates by 20\%.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst |HCL Technologies Client: Walmart}  \hfill \textbf{Jun2018 - Jun 2018}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Served as a bridge between product owners and development teams, ensuring acceptance criteria were clearly understood. This facilitated smoother communication and resulted in a 15\% reduction in misunderstandings and rework.}
\item {\small Mitigated and removed impediments encountered by the development team during sprints. Coordinated scrum sessions and meetings between value streams and scrum teams, leading to a 20\% increase in sprint completion rates.}
\item {\small Maintained documentation using Jira, Confluence, MS Teams, and SharePoint. Ensured artifacts were current and complete, improving document accessibility and accuracy by 25\%.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst | Wipro Technologies Client: Price Chopper - Market 32}  \hfill \textbf{Mar2010 - Jun2016}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Utilized Jira to track overall progress and coordinate with key stakeholders, achieving 100\% alignment with business needs and requirements. This streamlined the project workflow and improved stakeholder satisfaction by 20\%.}
\item {\small Defined the scope, gathered requirements, and performed GAP analysis, documenting artifacts on SharePoint. These efforts resulted in a 25\% reduction in requirement ambiguity and enhanced project clarity.}
\item {\small Generated MIS Dashboards and weekly reports using Tableau, providing actionable insights to the management team. This led to a 30\% improvement in decision-making processes and project tracking.}
\end{itemize}

\vspace{2mm}

\noindent \textbf{\underline{PROJECTS}} \\
\textbf{\textbf{Self-Checkout POS System }|PAtlassian Jira,Confluence, SharePoint,Power BI,Tableau,CRM} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Utilized Jira to track progress and coordinate with stakeholders, achieving 100\% alignment with business needs and a 20\% improvement in project workflow.
    \item Defined scope, gathered requirements, performed GAP analysis, and documented artifacts on SharePoint, reducing requirement ambiguity by 25\% and enhancing project clarity.


\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{CERTIFICATIONS}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Certified Scrum Product Owner CSPO, Safe v6.0 Scrum Master, ITIL V3.
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{ \underline {MEMBERSHIPS}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item PMI Toronto Chapter, Scrum Alliance, Scaled Agile, Axelos.
\end{itemize}


\end{document}
