\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\geometry{left=1cm, right=1cm, top=1cm, bottom=1cm}

\begin{document}

\begin{center}
    {\LARGE \textbf{Preksha Kulkarni}}\\
    \href{mailto:prekshakulkarni33@gmail.com}{prekshakulkarni33@gmail.com} \\
    \href{https://www.linkedin.com/in/prekshakulkarni/}{https://www.linkedin.com/in/prekshakulkarni/} \\
    \href{https://www.prekshakulkarni.com/}{https://www.prekshakulkarni.com/}
\end{center}

\vspace{0.5cm}

\section*{Work Experience}

\textbf{Indiana University, Indiana} \\
\textit{UX Researcher/Product Analyst} \\
August 2022 - May 2024
\begin{itemize}[left=0.15cm]
    \item Led user research efforts to refine an AI-driven pediatric cancer care application using mixed-method research, resulting in a 60\% reduction in error rates and improved adaptation rate by 30\%.
    \item Enhanced the product roadmap to address meal preparation pain points among college students through qualitative research (User Interviews and Contextual Inquiry) and delivered AI-integrated strategies to retain users.
    \item Developed 3 personas using qualitative research (20+ user interviews) with caregivers, prioritizing key features that addressed the key needs of caregivers.
    \item Achieved 85\% user satisfaction via mixed method research (15+ usability studies and surveys), ensuring the concept met user needs and expectations.
    \item Categorized users into 4 segments using K means clustering by analyzing census and lifestyle data which had over 1500 attributes and created 2 user personas, informing product roadmap.
    \item Identified behavioral trends of college students by tracking their food habits through Python scripts and Excel and produced trajectory reports for the next 10 years.
    \item Spearheaded identifying \& defining product KPIs to measure and leverage the behavioral data for data-driven decisions and using it for new product features.
    \item Developed a dashboard to track user behavior and needs, helping designers to make data-driven decisions.
    \item Led a 5-member team to handle project deliverables and performed 2 data visualization sessions for designers.
    \item Developed summary and detailed reports on caregivers using SAS to analyze their preferences and pain points.
\end{itemize}

\textbf{Dayforce, Indiana} \\
\textit{UX Researcher} \\
January 2024 - May 2024
\begin{itemize}[left=0.15cm]
    \item Led 30+ usability studies on the Wallet homepage, identifying confusing terms and visuals, which drove a redesign and renaming effort, resulting in a 55\% estimated increase in user comprehension and satisfaction for the Wallet app.
    \item Spearheaded cross-functional collaboration (product, design, research) to develop standardized UX research templates. Increased efficiency and ensured data consistency for on-site research across teams.
    \item Analyzed customer survey data to identify UX challenges across Dayforce products. Delivered usability scores and insights to leadership, influencing product roadmap decisions to improve North Star metrics.
\end{itemize}

\textbf{Coinbase, California} \\
\textit{UX Researcher} \\
May 2023 - September 2023
\begin{itemize}[left=0.15cm]
    \item Led user research for the asset buy flow, using 16+ user interviews and 2 sprig surveys, informing design improvements in the preview screen leading to increased user retention by 35\% and reduced drop-offs by 45\%.
    \item Improved limit order feature visibility in fund flow by 60\% for 7 million users, using 10+ usability studies and 8 moderated user interviews, boosting user engagement for the Coinbase simple trade platform on mobile.
    \item Spearheaded user research (10+ concept tests) to identify the top 5 features and inform the redesign of the trade tab, driving product roadmap improvements expected to increase user satisfaction and retention by 40\%.
\end{itemize}

\textbf{Ernst \& Young, India} \\
\textit{Product Analyst} \\
October 2020 - May 2022
\begin{itemize}[left=0.15cm]
    \item Owned the product roadmap for the global product hub of dashboards, prioritizing features and functionalities to facilitate seamless collaboration across international teams.
    \item Collaborated with product directors to define key performance indicators (KPIs), engineered data pipelines to deliver real-time insights on user engagement, and informed product decisions.
    \item Leveraged user engagement data to optimize marketing campaigns and inform data model redesigns, boosting brand awareness by 15\% and engagement by 75\%, strengthening the client base.
\end{itemize}

\textbf{Indian Institute of Management, Indore, India} \\
\textit{Research Intern} \\
June 2022 - July 2024
\begin{itemize}[left=0.15cm]
    \item Identified 50+ relevant business pedagogy articles, informing the development of the Integrative Live Case study.
    \item Introduced 10 new analytical variables, leading to a more comprehensive understanding of business education practices and influencing the development of new teaching strategies.
    \item Cross-referenced pedagogy and census data from over 1,000 records, refining insights for teaching strategy research and enabling the identification of key demographics for targeted educational approaches.
    \item Uncovered key trends in teaching methods through analysis of varied data, contributing to the development of innovative business education models that improved student learning outcomes.
\end{itemize}

\vspace{0.3cm}
\section*{Skills}
\textbf{Research \& Design:} User Interviews, Usability Study, Survey, Literature Review, Contextual Inquiry, Concept Testing, Card Sorting, Persona, Storyboarding, Information Architecture, Wireframing, Ideation, Participant Recruitment and Management, Research Scheduling and Planning, Research Repository, Competitive Analysis \\
\textbf{Business:} Product Strategy, Product Metrics, Market Analysis, Product Lifecycle Management, Product Roadmapping \\
\textbf{Tools:} Confluence, Figma, Power BI, Tableau, Jira, Dscout, UserTesting, Dovetail, Qualtrics, Python, R, SQL

\vspace{0.3cm}
\section*{Passion Projects}
\begin{itemize}[left=0.15cm]
    \item Sociostic - Facilitate the development of practical social interaction skills for students with high-functioning autism.
    \item Serious gaming for college students with ADHD
\end{itemize}

\vspace{0.3cm}
\section*{Awards}
\begin{itemize}[left=0.15cm]
    \item Ranked in the top 3 finalists for the Mira Awards under the Hunger Tech Challenge 2024.
    \item Won the “Brightest Engineer of India - 2020” award from the Economic Times.
\end{itemize}

\vspace{0.3cm}
\section*{Education}
\textbf{Indiana University, Indiana, US} \\
\textit{MS in Human-Computer Interaction} \\
August 2022 - May 2024 \\
\textbf{Medi-Caps University, India} \\
\textit{Btech in Computer Science} \\
August 2022 - May 2024

\end{document}
```

This LaTeX code will create a well-formatted resume based on the provided template and data. You can copy this code into your Overleaf project and compile it to see the output.