\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Kapil Gulani \\}
\normalsize \textbf{kapilgullani@gmail.com $\mid$ +1 9166959979 $\mid$ San Jose, CA  $\mid$ \href{https://kapilgulani.site/}{www.kapilgulani.site} $\mid$ \href{https://github.com/kapilgulani}{GitHub} $\mid$ \href{https://www.linkedin.com/in/kapil-gulani}{LinkedIn} \\}
\rule{\textwidth}{1pt}
\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{ Master of Science, Software Engineering } \hfill \textbf{Aug 2023 - Present} \\
\textIT{ San Jose State University, San Jose, CA}  
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\begin{itemize}
\end{itemize}
\textbf{Bachelor of Technology, Computer Science} \hfill \hfill \textbf{Aug 2017 - May 2021} \\
Medi-Caps University, India \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}{: \small Python (Pandas, NumPy, Matplotlib, Seaborn), R, SQL} \\
\textbf{Machine Learning}{: \small Linear Regression, Logistic Regression, Decision Trees, K-Means Clustering, PCA} \\
\textbf{DevOps and Version Control}{: \small Docker, Kubernetes, Docker Swarm, Terraform, AWS CloudFormation, Ansible, Git, GitHub, GitLab} \\
\textbf{Visualization Tools}{: \small Prometheus, Grafana, ELK Stack, AWS CloudWatch, Tableau, Power BI} \\
\textbf{Continuous Integration and Continuous Deployment (CI/CD)}{: \small Jenkins, GitLab CI, GitHub Actions} \\
\textbf{Cloud Platforms}{: \small AWS (EC2, S3, EMR, Lambda), Azure, Google Cloud Platform, Hadoop, Apache Kafka} \\
\textbf{Databases}{: \small MySQL, PostgreSQL, MongoDB, Redis} \\

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{DevOps Engineer | } Alpha Tech Solutions, India  \hfill \textbf{June 2021 – Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Automated and managed large-scale cloud infrastructure deployments using Docker, Kubernetes, and Terraform, significantly reducing system setup time and improving scalability across AWS, Azure, and GCP.}
\item {\small Designed and executed data-driven solutions with Python and R, utilizing libraries like Pandas and NumPy for data analysis and machine learning models, enhancing business decision-making and operational efficiency.}
\item {\small Developed and maintained robust CI/CD pipelines using Jenkins, GitLab CI, and GitHub Actions to streamline software delivery processes, which increased deployment frequency and reliability.}
\item {\small Implemented comprehensive monitoring solutions using Prometheus, Grafana, and the ELK Stack to ensure high availability and performance, reducing downtime and improving service responsiveness.}
\end{itemize}

\noindent \textbf{Software Engineer | } Beta Corp, India  \hfill \textbf{Jan 2020 - May 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Engineered and maintained scalable web applications using Microservices architecture, enhancing responsiveness and fault tolerance while integrating with Kafka for message brokering.}
\item {\small Enhanced data analytics capabilities by creating SQL and NoSQL solutions, supporting real-time data processing with MongoDB and Redis for improved application performance.}
\item {\small Led the implementation of automated testing and monitoring processes, which improved product quality and accelerated the development cycle.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
% Highlight integration of software engineering and DevOps practices
% Emphasize on automation, system reliability, and performance enhancements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{ARTLAND: E-Commerce Website -} \textit{Python Flask, MongoDB, Jenkins, Kubernetes} \hfill \textbf{Jan 2024 - Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Engineered an e-commerce platform using Python Flask; utilized MongoDB for robust data storage solutions and implemented scalable cloud infrastructure with Kubernetes.}
\item {\small Integrated advanced payment processing systems to enhance transaction security, combined with CI/CD pipelines using Jenkins for streamlined updates and deployment.}
\end{itemize}

\noindent \textbf{SIGNATURE VERIFICATION SYSTEM: -} \textit{React JS, Flask, YOLO v5, Siamese Networks} \hfill \textbf{Jan 2024 - Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a web application for real-time signature verification, integrating cutting-edge machine learning models including YOLO v5, ResNet, and Siamese Networks to enhance security and accuracy.}
\item {\small Implemented a responsive front-end using React JS, with a Flask and MongoDB backend, ensuring smooth operation and scalability under varying load conditions.}
\end{itemize}

\noindent \textbf{CINEXUS: Theater Management App -} \textit{Kotlin, Flask/Django, AWS, REST APIs} \hfill \textbf{Sep 2023 - Dec 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and deployed a cinema reservation system, utilizing Kotlin for the Android app and Python Flask/Django for backend operations, enhancing user experience and operational efficiency.}
\item {\small Hosted the application on AWS EC2, ensuring high availability and resilience, and integrated REST APIs for efficient communication between front-end and back-end systems.}
\end{itemize}

\noindent \textbf{GO-BIKE: Demand Forecasting -} \textit{Python, Scikit-learn, PyTorch, Keras, LSTM, DNN, Prophet} \hfill \textbf{Sep 2023 - Nov 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Created a demand prediction model for a bike-sharing service using advanced analytical techniques and machine learning models, including LSTM, DNN, and Prophet, significantly improving forecast accuracy.}
\item {\small Utilized Python and libraries such as Scikit-learn, PyTorch, and Keras to analyze historical data and optimize predictions, leading to more efficient resource allocation and enhanced user satisfaction.}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{}} \\
\noindent \textbf{\underline{AWARDS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small  Certified in the Python for Everybody Specialization by the University of Michigan, focusing on data structures, and application development. }
\end{itemize}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Secured 3rd place in a high-level Entrepreneurship-cell competition, demonstrating innovative capabilities. }
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\end{document}