%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
% Resume in Latex
% Author : Shubham Mazumder
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}

%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{flushleft}
    \textbf{\large Nagaraju Dasara} \\    
    \textit{Potsdam, NY, USA} $|$ 
    \textit{+1 (315) 603-7692} $|$  
    \href{mailto:nagarajudasara@gmail.com}{{\textit{Mail}}} $|$ 
    \href{https://www.linkedin.com/in/nagaraj-yadav/}{{\textit{Linkedin}}} $|$
    \href{https://github.com}{{\textit{Github}}}
    \vspace{-8pt}
\end{flushleft}

% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------

\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     {Experienced full-stack developer with a Master’s in Computer Science, specialized in automating complex systems using technologies like Python, Go, and Frameworks. Demonstrated ability to significantly boost system efficiency and functionality.} \\      
    }}
 \end{itemize}
 \sectionspace


% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\section{Awards and Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\titleItem{Finished in the top 10\% in National Science Examination conducted by IAPT.}}{2015}
      \resumeProjectHeading
          {\titleItem{Appeared in Final level NTSE and RMO Examinations.}}{2017}
      \resumeProjectHeading
          {\titleItem{Achieved 25th DSL rank in Math Scholarship Exam.}}{2014}
          \resumeProjectHeading
          {\titleItem{Distinctive participation in 7th International Mathematics Olympiad.}}{2013}
          \resumeProjectHeading
          {\titleItem{Distinctive participation in 4th International Mathematics Olympiad.}}{2010}
    \resumeSubHeadingListEnd
% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------

\section{Technical Skills}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \titleItem{Languages}{: C, C++, Python, Go, SQL, HTML/CSS} \\
     \titleItem{Expertise Area}{: Data Structures and Algorithms, Object-Oriented Programming (OOP), Parallel Programming} \\
     \titleItem{Tools and Frameworks}{: Docker, Kubernetes, Rabbitmq, Django, Flask, Powershell, Terraform, Numpy, Pandas, SciPy, Matplotlib} \\
     \titleItem{Machine Learning}{: Neural networks, CNN, Keras, Deep Learning, TensorFlow, OpenCV, Scikit-learn, Theano, PyTorch} \\
     \titleItem{Cloud Platforms}{: Microsoft Azure, AWS} \\
     \titleItem{Database}{: PostgreSQL, MSSQL Server, MongoDB, Redis} \\
     \titleItem{Continuous Integration/Continuous Deployment}{: Jenkins, GitHub Actions, GitLab CI/CD, Git}
    }}
 \end{itemize}
\sectionspace



    
% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Experience}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\titleItem{{Software Development Engineer}} $|$ \emph{Click2Cloud Inc.}}{October 2021 -- August 2023}
\resumeItemListStart
  \resumeItem{Drove automation for Agripilot.AI, integrating RabbitMQ as a message broker, enhancing system throughput and reducing message handling errors by 30\%. Developed modules in Go and Django.}
  \resumeItem{Developed a multi-cluster support feature for Fornax under CentaurusInfra, extending KubeEdge and built upon Kubernetes, using Go, which improved cluster management efficiency by 50\%.}
  \resumeItem{Enabled Windows Container support for nerdCTL, a Microsoft project for a Docker-like CLI, using Go, increasing platform compatibility and user adoption rates.}
  \resumeItem{Delivered a Data Lineage graph solution tailored to client requirements using Azure Logic Apps and Golang, optimizing data flow visualization and compliance tracking.}
  \resumeItem{Created a simulation tool in Python to model system behavior, enhancing predictive maintenance capabilities and reducing system downtime by 20\%.}
  \resumeItem{Developed an end-to-end automation script in Azure using PowerShell and Terraform, which reduced deployment times by 40\% and improved resource utilization.}
  \resumeItem{Developed a Python framework for managing multiple IoT devices concurrently, enhancing data stream handling and integration into analytics services and cloud storage.}
  \resumeItem{Contributed to ETL pipeline construction in Google Cloud Platform using Python, improving data processing speeds and accuracy by 25\%.}
  \resumeItemListEnd

\resumeProjectHeading
  {\titleItem{{Software Development Engineer Intern}} $|$ \emph{Mastersoft ERP Pvt Ltd}}{August 2020 -- February 2021}
\resumeItemListStart
  \resumeItem{Participated in all stages of the Software Development Life Cycle, including client demos, enhancing client engagement and feedback integration.}
  \resumeItem{Automated CSV generation and data manipulation scripts in Python, which streamlined data handling processes and reduced manual data entry errors by over 50\%.}
\resumeItemListEnd

\resumeSubHeadingListEnd


% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------

% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {University of Utah}{Salt Lake City, UT}
%       {MS in Computer Science | GPA: 3.86}{January 2021 -- December 2023} 
%     \resumeSubheading
%       {SRM University}{Chennai, TN, India}
%       {Bachelor of Technology in Computer Science and Engineering | GPA: 3.4}{August 2012 -- May 2016}
%   \resumeSubHeadingListEnd
% \vspace{-12pt}

\section{Education}    
    \resumeSubHeadingListStart
        \resumeProjectHeading
           {\titleItem{{Master of Science in Computer Science}} $|$ \emph{CGPA: 3.7/4.0}}{2023 -- Present}
           \resumeItem{{Clarkson University} $,$ \emph{Potsdam, NY, USA}}
        \resumeProjectHeading
           {\titleItem{{Bachelor of Technology in Computer Science and Engineering}}}{2017 -- 2021}
           \resumeItem{{Indian Institute of Information Technology} $,$ \emph{Nagpur, India}}
    \resumeSubHeadingListEnd



% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

 \section{Projects}    
     \resumeSubHeadingListStart
      \resumeProjectHeading
           {\titleItem{Defence Security System (Real Time)} $|$ \emph{Machine Learning, Artificial Intelligence, Python}}{December 2024}
            \resumeItemListStart
            \resumeItem{Developed a real-time defense security system capable of tracking and countering enemies using Python. Integrated Machine Learning and Artificial Intelligence to enable automation, significantly enhancing system responsiveness and operational efficiency.}
           \resumeItemListEnd
        \resumeProjectHeading
           {\titleItem{Identifying Disease Drug for Drug Repurposing using RWR} $|$ \emph{Python, TensorFlow, Machine Learning}}{September 2023}
            \resumeItemListStart
            \resumeItem{Developed a module using the Random Walk with Restart (RWR) algorithm in Python and TensorFlow to predict target genes for new diseases, showcasing advanced problem-solving and machine learning expertise.}
           \resumeItemListEnd
        \resumeProjectHeading
           {\titleItem{Car Parking Reservation System} $|$ \emph{C++, Object-Oriented Programming}}{June 2020}
            \resumeItemListStart
            \resumeItem{Built an object-oriented car parking system in C++, managing arrivals, displays, charges, and departures, demonstrating efficient real-world problem-solving with C++.}
           \resumeItemListEnd
       
     \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
