\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Devang Patidar \\}
\normalsize \textbf{02.Devapatidar@gmail.com $\mid$ +1 (732) 664-3401 $\mid$ \href{https://www.linkedin.com/in/devang-patidar-1b6b4a179}{Linkedin} $\mid$ \href{https://github.com/T0nyy0rk}{Github} \\}
\rule{\textwidth}{1pt}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Information Systems} \hfill \textbf{August 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD, USA}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\begin{itemize}
\end{itemize}
\textbf{Bachelor of Technology in Computer Science and Engineering} \hfill \textbf{August 2017 - May 2021} \\
\textit{Parul University, Vadodara, GJ, India} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}{: \small JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL, Java} \\
\textbf{Frontend Technologies}{: \small React.js, Next.js, Angular, Redux, Vue.js, Tailwind CSS} \\
\textbf{Backend Technologies}{: \small Node.js, Express.js, Spring Boot, Hibernate, Microservices, Rest API} \\
\textbf{Databases and Cloud}{: \small PostgreSQL, MongoDB, MySQL, SQLite, AWS (EC2, S3, Lambda), Google Cloud Platform, Firebase} \\
\textbf{Dev Tools and Operations}{: \small Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes,} \\
\textbf{Testing and APIs}{: \small Jest, Mocha, Cypress, RESTful Services, GraphQL, Apollo GraphQL, Postman, Swagger} \\
\textbf{Additional Skills}{: \small Responsive Web Design, Web Accessibility, Server-Side Rendering (SSR), WebSockets, OAuth, JWT} \\

% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}}\\
\noindent \textbf{Full Stack Developer | Webcraft IT, India} \hfill \textbf{2021 - 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and implemented responsive web designs with React.js and Tailwind CSS, improving the mobile user experience and increasing mobile traffic by 40\%.}
\item {\small Utilized PostgreSQL and MongoDB for robust data management, ensuring high performance and scalability of database operations.}
\item {\small Engineered microservices using Spring Boot and Hibernate, which improved modularity and streamlined updates and maintenance of backend services.}
\item {\small Implemented continuous integration and deployment pipelines using Jenkins and Kubernetes, which reduced deployment times by 50\% and increased deployment reliability.}
\item {\small Designed and tested RESTful services and GraphQL APIs using Postman and Apollo GraphQL, enhancing data interchange and integration across multiple platforms.}
\item {\small Employed AWS services such as EC2, S3, and Lambda to host applications and manage data storage, ensuring high availability and scalability of web applications.}\\
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Water Potability Analytics} \textit{Next.js, Python, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack water quality assessment tool using Python for backend data processing, MongoDB for data storage, and Next.js for the frontend. Deployed the application on AWS to ensure scalability and high availability.}
\end{itemize}

\noindent \textbf{Pizza Ordering Schema Optimization} \textit{Oracle PL/SQL, Next.js, Node.js, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Engineered a full stack solution for a pizza ordering system, designing the database schema with Oracle PL/SQL and implementing the user interface and server-side logic using Next.js and Node.js. Hosted the application on AWS for robust cloud-based operations.}
\end{itemize}

\noindent \textbf{Sales Insights for Brick \& Mortar Business} \textit{Power BI, SQL, React.js, Node.js, MongoDB} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Crafted a full stack BI tool for sales analysis, utilizing SQL for data management, React.js for dynamic frontend visualization, and Node.js with MongoDB for backend processing. Enhanced decision-making capabilities for business operations.}
\end{itemize}

\noindent \textbf{T20 World Cup Cricket Data Analytics} \textit{Python, Pandas, Next.js, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack cricket team selection tool, using Python and Pandas for data analysis, Next.js for the frontend, and MongoDB for data storage. Deployed on AWS to ensure performance and scalability during high traffic events like the T20 World Cup.}
\end{itemize}

\noindent \textbf{HR Data Analytics} \textit{Power BI, Excel, Next.js, Node.js, MongoDB} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and implemented a full stack HR dashboard using Next.js for the frontend, Node.js and MongoDB for backend operations, and Power BI for advanced data visualization, significantly streamlining HR operations.}
\end{itemize}

\noindent \textbf{Revenue Insights in the Hospitality Domain} \textit{Power BI, Excel, React.js, Node.js, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack dashboard to analyze revenue trends, using React.js for the frontend, Node.js for server-side logic, MongoDB for data handling, and AWS for deployment, providing crucial insights to recover revenue and market share.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small 2020: Awarded by Tops Technologies for excellence in Cyber Security}
\item {\small 2020: Recognized in the Discoveri Lite (Industry 4.0) program by SkillAssure}\\
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{Research}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small 2021: Published in the International Research Journal of Engineering and Technology (IRJET), Volume 8, Issue 4, April 2021. Title: "Food Recipes Recommendation System".}
\end{itemize}


\end{document}