\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Ashutosh Joshi \\}
\normalsize \textbf{\href{mailto:codewithashutxsh@gmail.com}{codewithashutxsh@gmail.com} $\mid$ \href{https://www.linkedin.com/in/ashutosh--joshi/}{LinkedIn} $\mid$ \href{https://github.com/ashutoshjoshi1}{Github} $\mid$ \href{https://ashutoshjoshi1.github.io/Portfolio/}{Portfolio} $\mid$ (415) 371-9354 $\mid$ United States \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Data Science} (GPA 3.8/4.0)  \hfill \textbf{August 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD}\\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\textbf{Bachelor of Technology in Computer Science} (GPA 3.7/4.0) \hfill \textbf{August 2016 - May 2020} \\
\textit{Medi-Caps University, Indore, India} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages}{: \small Python, .NET/C#, Java, HTML, XML, CSS, JavaScript, Redux, R, TypeScript, GoLang, Spark} \\
\textbf{Databases}{: \small SQL, MySQL, PostgreSQL, MongoDB, Oracle, Cassandra, Data Warehousing, Data Pipeline} \\
\textbf{Software}{: \small Microsoft SQL Server, VMware vSphere, Hyper V, Oracle, Jupyter, Matlab, Tableau, PowerBI, MS Office} \\
\textbf{Cloud Platforms}{: \small AWS, Microsoft Azure, Google Cloud Platform (GCP), Jenkins, Kubernetes, Docker, Terraform, TeamCity, Maven, JIRA, Agile/Scrum, Git, Distributed Systems, Spark} \\
\textbf{Technical Skills}{: \small Data Modeling, Custom ETL Development, System Resource Analysis, Flask, AngularJS, NodeJS, Spring Boot, TypeScript, ExpressJS, Selenium, JUnit, PostgreSQL, REST APIs, HDFS, MapReduce, UNIX, Linux, Hadoop} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Software Engineer Intern $\mid$ ZS, Bethesda, MD}  \hfill \textbf{June 2023 - April 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Transformed a multi-page web application into a high-performance single-page application using JavaScript and Redux, increasing revenue by \$2M. Implemented RESTful APIs with Node.js to handle 600,000+ user requests, enhancing responsiveness.}
\item {\small Overhauled backend for an ad-serving platform, improving load times by 20\% and user capacity to 40M with Node.js and Python. Enhanced R&D efficiency by 30\% through automated tools in Python and Django.}
\item {\small Streamlined software testing and debugging processes, boosting system efficiency by 25\% and ensuring robust operations.}
\end{itemize}

\vspace{2mm} 

\noindent \textbf{Graduate Student Assistant $\mid$ University of Maryland Baltimore County}  \hfill \textbf{January 2023 - December 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Led discussions and graded assignments for 50+ students, boosting educational support and success by 25\%.}
\item {\small Implemented Git for version control, enhancing assessment maintainability and increasing efficiency by 20\%.}
\item {\small Handled student inquiries and provided clarification, improving responsiveness by 25\%.}
\end{itemize}

\vspace{2mm} 

\noindent \textbf{Systems Engineer $\mid$ Tata Consultancy Services, India}  \hfill \textbf{June 2020 - August 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Utilized Agile methodologies to enhance the reliability and testability of portable and mobile two-way communication devices, reducing QA cycle times by 25\%.}
\item {\small Led a major cloud migration of over 2.7 terabytes with Azure Data Factory, improving organizational scalability and performance by 40\%.}
\item {\small Deployed Prometheus and Grafana for system monitoring, reducing resource use by 20\% and increasing data processing efficiency.}
\end{itemize}

\vspace{2mm} 

\noindent \textbf{Data Science Intern $\mid$ ThunderPod Inc, India}  \hfill \textbf{January 2020 - June 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and developed a machine learning model for a mobile application to accurately count exercise repetitions, such as push-ups and squats, achieving a 20\% improvement in accuracy.}
\item {\small Employed the PoseNet architecture to analyze and track human body poses in real-time, managing a large dataset of 175 GB.}
\item {\small Collaborated with a team of developers to integrate the machine learning model into the existing mobile app platform.}
\end{itemize}

\vspace{2mm} 

\noindent \textbf{Data Science Intern $\mid$ GenieTalk Pvt. Ltd, India}  \hfill \textbf{June 2019 - November 2019}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a natural language processing (NLP) model using machine learning techniques, resulting in a 30\% improvement in user interactions for ticket booking applications.}
\item {\small Integrated the NLP model into a Flask-based web application, leading to a 20\% increase in user engagement.}
\item {\small Utilized NLP techniques to enhance data analysis capabilities within the application's portal interface.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Diabetic Retinopathy Detection $\mid$ {\small Python, Heroku, Machine Learning, Data Modeling, Flask, REST APIs}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed and deployed a Python-based application on Heroku for medical image analysis, achieving over 90\% accuracy and a 95\% success rate in detecting diabetic retinopathy signs with a pre-trained model, supporting early detection for over 350 monthly active users.}
\item {\small Designed a responsive user interface with HTML and CSS, which improved user engagement by 30\% and facilitated easier access to analysis results.}\\
\end{itemize}


\noindent \textbf{ThunderCoach $\mid$ {\small Python, Motion Tracking, Flask, Data Modeling, REST APIs}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed an application to process videos at high frame rates using advanced pose estimation and motion tracking technologies, boosting workout effectiveness and user engagement.}
\item {\small Employed Python for 92\% accurate movement detection, which significantly improved exercise form identification and increased user consistency and technique.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \noindent \textbf{\underline{CERTIFICATIONS}}
% \begin{itemize}[noitemsep,nolistsep,leftmargin=*]
% \item {\small Azure Fundamentals - Associate $\mid$ Microsoft}
% \item {\small Machine Learning $\mid$ Stanford University}
% \item {\small Data Structures with Python $\mid$ University of Michigan}\\
% \end{itemize}



\end{document}
