\documentclass{article}

\usepackage[top=0.3in, bottom=0.2in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Preksha Kulkarni \\}
\normalsize California,USA $\mid$ +1 3177205929 $\mid$  \href{mailto:prekshakulkarni33@gmail.com}{Email} $\mid$ \href{https://www.linkedin.com/in/prekshakulkarni/}{Linkedin} $\mid$ \href{www.prekshakulkarni.com}{Website} \\
\hrulefill
\end{center}



% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Indiana University} \hfill  \\
\textit{MS in Human-Computer Interaction, Indiana, USA } $\mid$ GPA: 3.9 \hfill August 2022 - May 2024 \\ \\
\textbf{Medi-Caps University} \hfill  \\
\textit{BTech in Computer Science, India} $\mid$ GPA: 3 \hfill August 2016 - May 2020 

\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CORE SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\noindent \textbf{Research Method:} User Interviews, Usability Testing, Contextual Inquiry, Surveys, Concept Testing, Card Sorting, A/B Testing, Competitive Analysis, Eye Tracking, Tree Testing, Diary Studies, Focus Group, Regressive Analysis. \\
\noindent \textbf{Programming Languages:} Python, R, SQL, HTML, CSS. \\
\noindent \textbf{Design:} Persona, Storyboarding, Information Architecture, Wireframing, Ideation. \\
\noindent \textbf{Business:} Product Strategy, Product Metrics, Market Analysis, Product Lifecycle Management, Product Roadmapping. \\
\noindent \textbf{Tools:} Confluence, Jira, Trello, Asana, Slack, Dovetail, Qualtrics, Lookback, Figma, Sketch, Adobe XD, InVision, Balsamiq, Axure RP, Power BI, Tableau, Matplotlib, Seaborn.

\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{UX Researcher/Product Analyst $\mid$ Indiana University } \hfill \textbf{August 2022 - May 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
      \item Led user research using mixed-method approaches to refine an AI-driven pediatric cancer care application, reducing errors by 60\% and improving adaptation rates by 30\%. Enhanced the product roadmap, increasing student retention by 25\%.
    \item Developed 3 personas through qualitative research, increasing user engagement by 40\%. Used K-means clustering to create 2 user personas, informing the product roadmap and increasing feature adoption by 20\%.
    \item Identified trends in college students' food habits using Python and Excel, aiding strategic planning with 10-year reports. Defined product KPIs, leading to a 15\% improvement in performance.
    \item Created a dashboard to track user behavior, enabling data-driven design decisions and increasing efficiency by 30\%. Led a 5-member team and conducted 2 data visualization sessions, enhancing analytical skills.
\end{itemize}

\vspace{1mm}

\noindent \textbf{UX Researcher $\mid$ Dayforce} 
\hfill \textbf{Jan 2024 - April 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Led 30+ usability studies on the Wallet homepage, identifying terms and visuals. This resulted in a 55\% increase in user comprehension and satisfaction. Analyzed customer survey data to identify UX challenges, influencing product roadmap by 20\%.
    \item Spearheaded cross-functional collaboration to develop standardized UX research templates, increasing efficiency by 40\% and ensuring data consistency. Utilized Confluence and Jira for documentation and project management.
\end{itemize}


\vspace{1mm}

\noindent \textbf{UX Researcher $\mid$ Coinbase} 
\hfill \textbf{May 2023 - September 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Led asset buy flow research, conducting 16+ user interviews and 2 Sprig surveys, resulting in a 30\% increase in user retention and 45\% reduction in drop-offs. Improved limit order visibility by 60\% for 7 million users, boosting mobile engagement.
    \item Spearheaded research to identify the top 5 features for the trade tab redesign, expected to increase user satisfaction and retention by 40\%. Conducted user interviews, surveys, and contextual inquiry.
\end{itemize}

\vspace{1mm}

\noindent \textbf{Product Analyst $\mid$ Ernst \& Young} 
\hfill \textbf{October 2020 - May 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Owned the product roadmap for the global dashboards hub, enabling international team collaboration with Jira and Confluence. Defined KPIs with directors and built data pipelines for real-time user insights, improving decision-making speed by 20\%.
    \item Optimized marketing campaigns by leveraging user engagement data, boosting brand awareness by 15\% and engagement by 75\%. Utilized analytics tools such as Google Analytics and Tableau for data visualization and analysis.
\end{itemize}

\vspace{1mm}

\noindent \textbf{Research Intern $\mid$ Indian Institute of Management, Indore} 
\hfill \textbf{June 2019 - July 2019}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Identified 50+ business pedagogy articles to develop the Integrative Live Case study, boosting student engagement by 25\%. Introduced 10 new variables, enhancing teaching effectiveness by 20\% through qualitative and quantitative analysis.
    \item Cross-referenced pedagogy and census data from over 1,000 records, refining insights for teaching strategy research and enhancing strategy accuracy by 30\%. Utilized data analysis tools such as Python and Excel.
\end{itemize}

\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Sociostic $\mid$ Python, R, Data Analysis, Behavioral Research} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Facilitated the development of practical social interaction skills for students with high-functioning autism, resulting in a 40\% improvement in social engagement.
    \item Implemented a feedback loop with educators and parents, leading to a 30\% increase in the effectiveness of social skill interventions.
\end{itemize}

\noindent \textbf{Serious Game $\mid$ Unity, HTML, CSS, A/B Testing} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
    \item Developed serious games for college students with ADHD, enhancing focus and task completion rates by 35\%. Conducted A/B testing and gathered feedback from 50+ users to optimize game mechanics and usability.
    \item Collaborated with mental health professionals to integrate evidence-based techniques, increasing user satisfaction by 25\%.
\end{itemize}

\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXTRA SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS}} \\
\noindent \textbf{Mira Awards} $\mid$ Ranked in the top 3 finalists for the Mira Awards under the Hunger Tech Challenge 2024.

\noindent \textbf{Brightest Engineer of India} $\mid$ Won the “Brightest Engineer of India - 2020” award from the Economic Times.

    

\end{document}