\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Jayesh Jaywant Naik \\}
\normalsize \textbf{\href{mailto:jayeshjaywantnaik@gmail.com}{jayeshjaywantnaik@gmail.com} $\mid$ +1 667-232-1540 $\mid$ \href{https://www.linkedin.com/in/jayeshjnaik}{LinkedIn} $\mid$ \href{https://github.com/jayeshjnaik}{GitHub} \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science, Information Systems } \hfill \textbf{Aug 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD (GPA: 3.9/4)}  
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\begin{itemize}
\end{itemize}
\textbf{Bachelor of Engineering, Computer Science} \hfill \textbf{Aug 2017 - Jul 2021} \\
\textit{Mumbai University, Mumbai, India (GPA: 4.0/4)}\\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages}{: \small SQL, Python, R, Java, Bash, HTML, CSS} \\
\textbf{Machine Learning and Data Analysis Tools}{: \small Pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch, Excel, SPSS, SAS} \\
\textbf{Business Intelligence Tools}{: \small Tableau, Power BI, Looker, Google Data Studio, SAS Visual Analytics, Qlik} \\
\textbf{Data Engineering Tools}{: \small Apache Kafka, Apache Flink, Jenkins, Docker, Kubernetes, Cloudera, Snowflake} \\
\textbf{Databases}{: \small PostgreSQL, MySQL, MongoDB, SQLite, Redis, Elasticsearch, DynamoDB, Oracle, Microsoft SQL Server} \\
\textbf{Developer Tools}{: \small Git, Jupyter, RStudio, BitBucket, GitLab, Terraform, Postman, AWS Data Pipeline, Databricks} \\
\textbf{Data Management \& Integration}{: \small Informatica, Talend, DataStage, Stitch, Fivetran}
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Data Analyst | Artisan Desired Solutions, Mumbai, India}  \hfill \textbf{June 2020 – July 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Leveraged data analysis techniques using Python libraries and SQL queries to analyze booking system data. This analysis identified opportunities to improve data consistency by 15\% through API optimization and enhanced collaboration practices.}
\item {\small Lead for the development of TrainBookingSuvidha using ReactJS. Employed Agile/Scrum methodology to manage the project, while concurrently analyzing user feedback and booking data to guide development efforts. This data-driven approach resulted in a 20\% increase in user satisfaction with the ticket booking process.}
\item {\small Performed data analysis on booking system reports using Python libraries Pandas and Scikit-learn to identify trends and patterns. Created search filters for collaborative admin reports using LINQ, enabling efficient data retrieval by 30\% improvement and streamlined data processing operations.}
\item {\small Collaborated with DevOps engineers to implement Azure pipelines and SVN Tortoise for software deployment. Analyzed deployment logs and system metrics to identify performance bottlenecks, leading to a 40\% reduction in deployment time.}
\item {\small Utilized Entity Framework for CRUD operations on SQL Server data. Analyzed database performance metrics to identify optimization opportunities, resulting in a 25\% improvement in query performance.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Data Analyst Intern | Eduvance, Mumbai, India}  \hfill \textbf{June 2019 – June 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and developed user interfaces (UIs) using HTML, CSS, and JavaScript. Analyzed user behavior data, clickstream data to identify areas for UI optimization, leading to a 70\% reduction in page load times and improved performance.}
\item {\small Collaborated with software developers to build web applications. Extracted and analyzed data from various sources (databases, web forms) using SQL and Python (Pandas). The insights gained were used to create user interfaces (HTML, JavaScript) that efficiently retrieved and displayed data, resulting in a 50\% improvement in data retrieval efficiency and a 45\% increase in user satisfaction.}
\item {\small Analyzed business requirements and user data to design and implement database scripts, stored procedures, and triggers. This streamlined data processing by 60\% and reduced data-related errors by 75\%, improving overall data quality and system reliability.}
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} 

\noindent \textbf{Crowd Analysis System $\mid$ Python, Computer Vision, Image Processing, ML, OpenCV} \textit{\hfill \textbf{August 2021}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Leveraged Python libraries like OpenCV for image processing techniques (opening and closing) to transform images into human-like shapes after background subtraction. This approach led to a 25\% improvement in crowd detection accuracy.}
  \item {\small Developed a real-time people counting system using computer vision algorithms. This system facilitated efficient crowd management and ensured adherence to safety protocols by enabling a 30\% reduction in response time.}
  \item {\small Designed a low-cost, non-intrusive system using ML to collect real-time crowd data and measure the flow of people through a location.}
\end{itemize}
\vspace{1mm} 
\noindent \textbf{Shopping Website Development $\mid$ ReactJS, Redux, API, Axios, Kafka, Docker} \textit{\hfill \textbf{December 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Implemented Redux for efficient state management, providing a scalable foundation for the shopping application. This ensured consistent data flow and simplified component updates.}
  \item {\small Developed a set of responsive and user-friendly React components to deliver an intuitive shopping experience. These components ensured the website adapts to different screen sizes and provides a seamless user interaction.}
  \item {\small Utilized Axios to make API calls and populate the Redux store with real product data, ensuring dynamic content updates and reflecting the latest product information.}
  \item {\small Integrated Redux DevTools to streamline debugging and development processes, enhancing overall project maintainability. This allowed for easier identification and resolution of issues during development.}
\end{itemize}
\vspace{1mm} 
\noindent \textbf{Tic Tac Toe Game $\mid$ React, React Hooks, Fetch, NodeJS, MySQL, API Integration} \textit{\hfill \textbf{August 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Built a real-time multiplayer Tic Tac Toe game using React and React Hooks.}
  \item {\small Designed a NodeJS backend for game synchronization and MySQL for user profiles and leaderboards.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
