Here is the resume converted into the provided LaTeX template:

```latex
\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Vartika Jain \\}
\normalsize vartikajainvps@gmail.com $\mid$ +91 9571443886 $\mid$ www.linkedin.com/in/vartikajai \\
\hrulefill
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{OBJECTIVE}} \\
\noindent Graduate student looking for finance and marketing positions starting immediately. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{CORE SKILLS}} \\
Operations Management (4 years), Research Analysis (1 year), Wealth Management (6 months) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{JECRC University} \hfill Jaipur, Rajasthan \\
\textit{Master of Business Administration (MBA) in Finance & Marketing} \hfill Completed \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Vardhman Electro Power Industries} \hfill Jaipur, Rajasthan \\
\textit{Operations Manager and Administrator} \hfill Sep 2019 - Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Experienced backoffice professional skilled in optimizing operations, reducing errors, and driving efficiency.
\item Proven ability to identify and resolve complex problems, implementing strategic initiatives to streamline operations and enhance service delivery.
\item Designed & developed reports and dashboards using the Power BI platform.
\item MIS/Reporting regarding tracking sale, inventory equipments and Electro market information.
\item Performance-oriented operations professional emphasizing efficiency and accuracy.
\item Demonstrated expertise in overseeing complete processes, optimizing workflows, and effectively leading projects.
\item Proficient in implementing strategic solutions to elevate operational efficiency.
\item Maintained general finances & budgeting. \\
\end{itemize}

\noindent \textbf{Absas Solutions Private Limited} \hfill Jaipur, Rajasthan \\
\textit{Research Associate} \hfill Jan 2019 - Sep 2019
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Gathered, arranged, and corrected research data to create representative graphs, charts, dissertations, and reports highlighting results for presentations.
\item Proficient in data collection, organization, and analysis, utilizing advanced techniques to produce insightful graphs, charts, and reports that effectively communicate research findings.
\item Skilled in data correction and validation, ensuring accuracy and reliability of research data for generating informative dissertations and presentations. \\
\end{itemize}

\noindent \textbf{AU Small Finance Bank} \hfill Jaipur, Rajasthan \\
\textit{Wealth Management Intern} \hfill Feb 2018 - Jul 2018
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Collaborated in implementing a wide range of technical and non-technical initiatives across the wealth management group, demonstrating adaptability and proficiency in project execution.
\item Offered comprehensive operational support to management, efficiently responding to time-sensitive firm-level or client-driven events, and employing strong analytical skills for client reporting and analytics.
\item Designed & developed MIS Reports for the wealth management team.
\item Assisted clients with their standard transactional needs, including processing deposits, payments, transfers, and other routine transactions, showcasing exceptional customer service and financial acumen. \\
\end{itemize}

\noindent \textbf{Integral Urban Cooperative Bank} \hfill Jaipur, Rajasthan \\
\textit{Banking Intern} \hfill May 2017 - Jul 2017
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Provided comprehensive support to daily operations and processes, effectively contributing to the achievement of sales and service goals.
\item Welcomed and engaged with customers in the bank lobby, ensuring a positive and customer-centric experience while addressing and resolving any inquiries or issues.
\item Assisted customers with a wide range of service needs, including product explanations and various banking transactions, delivering exceptional service and fostering customer satisfaction. \\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Project Name} \textit{Course Name} \hfill  Month, Year $-$ Month, Year
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed XYZ using XYZ that led to X\% improvement.
\item Led an initiative XYZ to identify the root cause.
\item Collaborated with XYZ team to work on XYZ feature. \\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EXTRA SECTION}} \\
\noindent \textbf{Activity/ Role} \hfill Month, Year $-$ Month, Year
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item What did you do, how did you do it and what did you achieve? \\
\end{itemize}

\noindent \textbf{Activity/ Role} \hfill Month, Year $-$ Month, Year
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item What did you do, how did you do it and what did you achieve? \\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{OTHER SKILLS}} \\
\noindent \textbf{Technical Skills:} Power BI, Turnitin, Finacle, MS Office Suite \\
\noindent \textbf{Management Skills:} Team Leadership, Financial Reporting, MIS/Reporting, Financial Analyst, Expert in Communication \\

\end{document}
```

This LaTeX code includes the information from the provided PDF resume in the specified template.