\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{AASISH KUMAR IMMADISETTY \\}
\normalsize Washington DC.USA$\mid$iaasish123@gwu.edu$\mid$(202)6157919 $\mid$ \href{https://www.linkedin.com/in/aasish-kumar-i-944384167/}{Linkedin}   \\
\hrulefill
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{The George Washington University} \hfill Washington, DC \\
\textit{Master of Science in Data Science}  GPA:3.84 \hfill August 2021 - May 2023 \\ \\
\textbf{PES University} \hfill Bengaluru, India \\
\textit{Bachelor of Technology in Information Science \& Engineering}  GPA: 3 \hfill August 2014 - May 2018 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL SKILLS}} \\
\textbf{Languages:} SQL, Python, R, Bash, HTML, CSS \\
\textbf{Data Analysis Tools:} Pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch, Excel, SPSS, SAS \\
\textbf{Business Intelligence Tools:} Tableau, Power BI, Looker, Google Data Studio, SAS Visual Analytics, Qlik \\
\textbf{Data Engineering Tools:} Apache Kafka, Apache Flink, Jenkins, Docker, Kubernetes, Cloudera, Snowflake \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, Elasticsearch, DynamoDB, Oracle, Microsoft SQL Server \\
\textbf{Developer Tools:} Git, Jupyter, RStudio, BitBucket, GitLab, Terraform, Postman, AWS Data Pipeline, Databricks \\
\textbf{Data Management \& Integration:} Informatica, Talend, DataStage, Stitch, Fivetran\\

% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentor and mentees for Android and iOS platform.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{George Washington University} \hfill Washington, D.C \\
\textit{Technology Associate} \hfill July 2023 – Present
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Reported project status to management, highlighting risks, challenges, and critical decisions. Identified project risks,implemented mitigation plans, leading to a 40\% reduction in project delays and a 30\% improvement in project.}
\item {Utilized Python, Power BI, and ETL processes to transform and visualize data. Processed massive datasets containing millions of records, such as student information and fee payments, resulting in a 50\% improvement in data processing speed and a 35\% increase in data accuracy.}
\item {Generated reports and created compelling visualizations using Python modules, including graphs and dashboards. Effectively reduced costs by 20\% through the efficient.}
\vspace{1mm}
\end{itemize}

\noindent \textbf{Ericsson} \hfill Bengaluru, India \\
\textit{Data Analyst} \hfill October 2018 - August 2021
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Collaborated with the data engineering team to migrate on-premises SQL databases to Azure using Azure Data Factory and Azure Data Migration Service. Utilized matrix algebra for cluster size estimation and optimization, resulting in a 40\% reduction in migration time and 25\% decrease in resource usage.}
\item {Actively contributed to the development of branching strategies in Azure DevOps, ensuring a well-structured and efficient pipeline from development through testing to production environments. This contributed to a 30\% increase in deployment speed and a 20\% reduction in deployment errors.}
\item { Identified dimension and fact tables and designed a data warehouse using the star schema approach. This design improved query performance by 35\% and reduced data redundancy by 50\%.}
\item {Reviewed and optimized SQL queries, stored procedures, functions, indexes, views, and triggers. These optimizations resulted in a 45\% improvement in query execution time and a 30\% increase in overall database performance.\\}

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about team work, initiative, soft skills.
%
% Can also include personal projects, competitions, contribution to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Deprived Area Mapping} $\mid$\textit{Python, GIS, Plotly, Dash} \hfill  March 2023 -May 2023
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Engineered machine learning models, achieving 83.5\% accuracy in predicting socio-economic indicators in Nairobi's deprived areas. Utilized GIS tools for spatial analysis, enhancing resource allocation efficiency by 20\% for government stakeholders.}
\item {Created interactive dashboards with Plotly and Dash for real-time socio-economic data visualization, increasing decision-making speed by 25\% and improving data accessibility by 30\% for urban development initiatives.}
\end{itemize}

\noindent \textbf{Fake and Real News Dataset} \textit{Python, Flask, Pandas, NumPy} \hfill  October 2022 – December 2023
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {Tuned algorithm parameters and experimented with NLP models (DistillBert, DeBERTa, and RoBERTa) to enhance classification accuracy, achieving 98\% accuracy on a subset of news articles and reducing errors by 50\%.}
\item {Developed a web application using Flask to deploy the trained model, enabling users to input news articles and receive real-time authenticity predictions. achieving a user satisfaction rate of 95\%.}
\end{itemize}

\noindent \textbf{Netflix Movie/Tv shows} \textit{Tableau, SQL, Excel} \hfill  March 2022 - May 2022
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item { Leveraged Tableau to create visualizations of movie and TV show performance across various countries, providing insights that led to a 15\% increase in user engagement worldwide.}
\item {Conducted numerical data analysis using mathematical operations, including manipulation of numbers and matrices, to extract insights and support decision-making processes, resulting in a 20\% improvement in strategic decision accuracy.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{document}
