%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}

%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{flushleft}
    \textbf{\large Ishan Joshi} \\    
    \textit{Baltimore, United States} $|$ 
    \textit{+1 (551) 344-7885‬} $|$  
    \href{mailto:ishan.joshiapplication@gmail.com}{{\textit{Email}}} $|$ 
    \href{https://www.linkedin.com/in/ishanjoshi6286/}{{\textit{linkedin}}} $|$
    \href{https://123ishan.github.io/portfolio/}{{\textit{github}}}
    \vspace{-8pt}
\end{flushleft}

% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------

\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     {Experienced data analyst with over 5 years of expertise in data processing and visualization, delivering insightful and analytics. Strong problem-solving skills and a proven ability to communicate complex data findings effectively to drive business decisions.} \\      
    }}
 \end{itemize}
 \sectionspace


% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

% \section{Awards and Certifications}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\titleItem{Star Award} \emph{ $|$ Company 1}}{September 2018}
%       \resumeProjectHeading
%           {\titleItem{Kudos Award} \emph{ $|$ Company 2}}{May 2017}
%       \resumeProjectHeading
%           {\titleItem{IBM Full Stack Software Developer} \emph{$|$ IBM}}{November 2023}
%           \resumeProjectHeading
%           {\titleItem{CompTia Sec+} \emph{$|$ CompTia}}{December 2023}
%     \resumeSubHeadingListEnd
% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------

\section{Technical Skills}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \titleItem{Programming Languages}{: Python (Pandas, NumPy, Matplotlib, Seaborn, SciPy), R, Scala} \\
     \titleItem{Data Processing}{: Apache Spark, Apache Airflow, Apache Kafk, Hadoop, Apache Flink} \\
     \titleItem{Cloud Platforms}{: AWS, Azure, Google Cloud Platform (BigQuery, Dataflow, Cloud Storage)} \\
     \titleItem{Databases and Data Warehousing}{: MySQL, PostgreSQL, MongoDB, Redis, Snowflake, DynamoDB} \\
     \titleItem{Data Visualization Tools}{: Prometheus, Grafana, ELK Stack, AWS CloudWatch, Tableau, Power BI, Apache Superset, Looker} \\
     \titleItem{Version Control and CI/CD}{: Git, GitHub, GitLab, Jenkins} \\
    }}
 \end{itemize}
\sectionspace





    
% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
         {\textbf{Data Analyst} $|$ \emph{Holland America Group}, Seattle, WA}{May 2023 - September 2023}
    \resumeItemListStart
      \resumeItem{Analyzed and interpreted complex data sets using SQL and Python (Pandas, NumPy), identifying key trends that influenced strategic decisions and resulted in a 15\% increase in operational efficiency. Integrated Apache Spark for large-scale data processing and employed visualization tools like Tableau and Power BI.}
      \resumeItem{Managed and optimized data processes over 2 TB using Hadoop and Apache Kafka for real-time data streaming, enhancing marketing strategies through effective data manipulation and extraction.}
      \resumeItem{Conducted multi-dimensional data analysis integrating SQL, Python, and Tableau for comprehensive business intelligence and customer insights, significantly boosting sales metrics. Used Looker for additional data visualization support.}
      \resumeItem{Developed predictive models and automated data pipelines using SQL, Python, R, and Apache Airflow, enhancing business decision-making processes and operational responsiveness.}
    \resumeItemListEnd
    \vspace{.5mm}
    \resumeProjectHeading
         {\textbf{Senior Software Development Engineer} $|$ \emph{Volkswagen Group IT Services}, India}{September 2019 -- September 2022}
    \resumeItemListStart
      \resumeItem{Architected and deployed scalable microservices using Java and Scala with Spring Boot, incorporating Docker and Kubernetes for container management and orchestration, leading to improved system resilience and efficiency. Managed version control using Git and GitHub.}
      \resumeItem{Led the front-end and back-end development of an SLA Tracker using React.js and Node.js, integrating RESTful APIs and utilizing Jenkins for CI/CD, achieving project goals under budget and enhancing service reliability.}
      \resumeItem{Supervised a cross-functional development team employing Agile methodologies and continuous integration/continuous deployment (CI/CD) practices with GitLab to speed up delivery and enhance product quality.}
      \resumeItem{Optimized front-end performance by implementing state management solutions in React, improving user engagement and operational efficiency through enhanced UI/UX designs, and using AWS CloudWatch for performance monitoring.}
    \resumeItemListEnd
    \vspace{.5mm}
    \resumeProjectHeading
         {\textbf{Web Development Intern} $|$ \emph{Spring Jaunter}, India}{January 2019 -- March 2019}
    \resumeItemListStart
      \resumeItem{Engineered and deployed a full-stack solution using React.js and Node.js, focusing on streamlining operational processes through automated solutions and advanced web technologies. Implemented MongoDB for data management and used Apache Flink for stream processing.}
      \resumeItem{Contributed to a major e-commerce platform overhaul, improving system architecture and enhancing front-end features using HTML5, CSS3, and JavaScript to elevate user experience and conversion rates. Employed Prometheus and Grafana for real-time analytics and monitoring.}
      \resumeItem{Developed custom internal applications focusing on productivity improvements, employing modern JavaScript frameworks and server-side technologies to automate routine tasks effectively. Integrated AWS services for cloud-based data handling.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd




% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------

% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {University of Utah}{Salt Lake City, UT}
%       {MS in Computer Science | GPA: 3.86}{January 2021 -- December 2023} 
%     \resumeSubheading
%       {SRM University}{Chennai, TN, India}
%       {Bachelor of Technology in Computer Science and Engineering | GPA: 3.4}{August 2012 -- May 2016}
%   \resumeSubHeadingListEnd
% \vspace{-12pt}

\section{Education}    
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\titleItem{{Master Of Science In Information Systems}} $|$ \emph{3.7}}{August 2022 -- May 2024}
           \resumeItem{{University of Maryland} $,$ \emph{Baltimore, MD, USA}}
       \resumeProjectHeading
           {\titleItem{{Bachelor of Engineering in Computer Science}} $|$ \emph{3.9}}{July 2015 -- May 2019}
           \resumeItem{{Pune University} $,$ \emph{Pune, India}}
     \resumeSubHeadingListEnd

% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

 \section{Projects}    
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\textbf{Automatic Diagnosis of Quantum Software Bug-Fix} $|$ \emph{Python, Algorithm Development, Predictive Analytics}}{\href{https://tinyurl.com/GITQUNTUM}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Developed a Python-based diagnostic tool for quantum software, utilizing predictive analytics and real-time data processing with Apache Kafka to reduce bug resolution time by 50\%.}
           \resumeItemListEnd
       
        \resumeProjectHeading
           {\textbf{Water Potability Analysis} $|$ \emph{Python, Data Cleaning, Predictive Modeling, Hypothesis Testing}}{\href{https://github.com/123Ishan/Water-Potability}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Analyzed water quality using Python in Jupyter, applying feature engineering and predictive modeling to ensure compliance; enhanced data visualization with Tableau.}
           \resumeItemListEnd
           
        \resumeProjectHeading
           {\textbf{Deep Learning Model for Diabetic Retinopathy} $|$ \emph{Machine Learning, Python, Image Processing, Data Preprocessing}}{\href{https://github.com/123Ishan/Diabatic-Retenipathy-Detection}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Created a deep learning model for diagnosing diabetic retinopathy, using Python for data preprocessing and feature extraction; evaluated model using accuracy and precision metrics.}
           \resumeItemListEnd
     \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
