\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\documentclass{article}
\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Amisha Garg \\}
\normalsize New York, United States $\mid$ +1(229)4626192 $\mid$ \href{mailto:mail@example.com}{mail@example.com} $\mid$ \href{https://www.linkedin.com/in/your-linkedin}{LinkedIn} $\mid$ \href{https://github.com/your-github}{GitHub} \\
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science, Information Systems } \hfill \textbf{Aug 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD (GPA: 3.9/4)}  
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}


\textbf{Bachelor of Engineering, Computer Science} \hfill \textbf{Aug 2017 - Jul 2021} \\
\textit{Mumbai University, Mumbai, India (GPA: 4.0/4)}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}{: \small Python, C++, Java, SQL, PL/SQL, JavaScript, TypeScript, Go, Vue, HTML, XML, CSS, R} \\
\textbf{Frontend Technologies}{: \small React.js, Next.js, Angular, Redux, Vue.js, Tailwind CSS} \\
\textbf{Backend Technologies}{: \small Node.js, Express.js, Spring Boot, Hibernate, Microservices, Rest API} \\
\textbf{Databases and Cloud}{: \small PostgreSQL, MongoDB, MySQL, SQLite, AWS (EC2, S3, Lambda), Google Cloud Platform, Firebase} \\
\textbf{Dev Tools and Operations}{: \small Git, GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes,} \\
\textbf{Testing and APIs}{: \small Jest, Mocha, Cypress, RESTful Services, GraphQL, Apollo GraphQL, Postman, Swagger} \\
\textbf{Additional Skills}{: \small Responsive Web Design, Web Accessibility, Server-Side Rendering (SSR), WebSockets, OAuth, JWT}
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Data Analyst | Insightful Data Solutions, Mumbai, India}  \hfill \textbf{June 2020 – July 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Analyzed customer booking data using SQL, Python, and Pandas, identifying key trends and insights that contributed to a 40\% increase in user engagement and a 30\% boost in bookings.}
\item {\small Leveraged statistical analysis techniques in R to uncover patterns in user behavior, leading to a 50\% improvement in data throughput and enhancing decision-making processes.}
\item {\small Developed interactive data visualizations using Tableau, effectively communicating complex findings to stakeholders and facilitating data-driven decision-making.}
\item {\small Implemented predictive models using Scikit-learn and TensorFlow to forecast booking demand, resulting in a 60\% reduction in inventory costs while maintaining service levels.}
\item {\small Conducted A/B testing on the booking platform using statistical hypothesis testing, driving a 55\% improvement in user satisfaction and retention rates.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Data Analyst Intern | Data Insights Consulting, Mumbai, India}  \hfill \textbf{June 2019 – July 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Cleaned and transformed large datasets using Python and SQL, improving data accuracy and reliability by 65\% and enabling more accurate analysis.}
\item {\small Developed and deployed machine learning models for sentiment analysis of customer reviews, leading to a 50\% reduction in negative feedback and improved customer satisfaction.}
\item {\small Utilized Power BI to create interactive dashboards for monitoring key performance indicators, resulting in a 45\% increase in operational efficiency.}
\item {\small Conducted exploratory data analysis on market trends using NumPy and Matplotlib, providing actionable insights for strategic decision-making.}
\item {\small Collaborated with cross-functional teams to identify data-driven solutions to business challenges, resulting in a 40\% increase in revenue and profitability.}
\end{itemize}




\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECT WORK}} 

\noindent \textbf{Crowd Analysis System $\mid$ Python, Computer Vision, Image Processing, ML, OpenCV} \textit{\hfill \textbf{August 2021}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Developed a real-time people counting system using computer vision algorithms, which facilitated efficient crowd management and ensured adherence to safety protocols by enabling a 30\% reduction in response time.}
  \item {\small Designed a low-cost, non-intrusive system using machine learning to collect real-time crowd data and measure the flow of people through a location, enhancing the system's functionality and user accessibility.}
  \item {\small Implemented advanced image processing techniques using OpenCV to accurately detect and analyze crowd density in various environmental conditions, significantly improving the precision of crowd assessments.}
\end{itemize}
\vspace{1mm} 

\noindent \textbf{Shopping Website Development $\mid$ ReactJS, Redux, API, Axios, Kafka, Docker} \textit{\hfill \textbf{December 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Implemented Redux for state management across the shopping application, providing a robust and scalable foundation that ensured consistent data flow and simplified component updates.}
  \item {\small Developed responsive and user-friendly React components to deliver an intuitive shopping experience, ensuring the website adapts to different screen sizes and provides seamless user interaction.}
  \item {\small Utilized Axios to make dynamic API calls and populate the Redux store with real product data, reflecting the latest product information and ensuring dynamic content updates.}
\end{itemize}
\vspace{1mm} 

\noindent \textbf{Tic Tac Toe Game $\mid$ React, React Hooks, Fetch, NodeJS, MySQL, API Integration} \textit{\hfill \textbf{August 2020}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
  \item {\small Integrated RESTful APIs using NodeJS to facilitate real-time communication between the client and server, ensuring efficient data transfer and state updates, which drastically improved the responsiveness and interactivity of the game.}
  \item {\small Designed a robust NodeJS backend for game synchronization and employed MySQL for managing user profiles and leaderboards, enhancing game functionality and user engagement.}
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
