\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Devang Patidar \\}
\normalsize \textbf{02.Devapatidar@gmail.com $\mid$ +1 (732) 664-3401 $\mid$ \href{https://www.linkedin.com/in/devang-patidar-1b6b4a179}{Linkedin} $\mid$ \href{https://github.com/T0nyy0rk}{Github} \\}
\rule{\textwidth}{1pt}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Information Systems} \hfill \textbf{August 2022 - May 2024} \\
\textit{University of Maryland Baltimore County, Baltimore, MD, USA}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\begin{itemize}
\end{itemize}
\textbf{Bachelor of Technology in Computer Science and Engineering} \hfill \textbf{August 2017 - May 2021} \\
\textit{Parul University, Vadodara, GJ, India} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Programming Languages}{: \small Python (Pandas, NumPy, Matplotlib, Seaborn), R, SQL} \\
\textbf{Machine Learning}{: \small Linear Regression, Logistic Regression, Decision Trees, K-Means Clustering, PCA} \\
\textbf{DevOps and Version Control}{: \small Docker, Kubernetes, Docker Swarm, Terraform, AWS CloudFormation, Ansible, Git, GitHub, GitLab} \\
\textbf{Visualization Tools}{: \small Prometheus, Grafana, ELK Stack, AWS CloudWatch, Tableau, Power BI} \\
\textbf{Continuous Integration and Continuous Deployment (CI/CD)}{: \small Jenkins, GitLab CI, GitHub Actions} \\
\textbf{Cloud Platforms}{: \small AWS (EC2, S3, EMR, Lambda), Azure, Google Cloud Platform, Hadoop, Apache Kafka} \\
\textbf{Databases}{: \small MySQL, PostgreSQL, MongoDB, Redis} \\

% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}}\\
\noindent \textbf{DevOps Engineer | Webcraft IT, India} \hfill \textbf{2021 - 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Orchestrated containerized environments using Docker and Kubernetes, enhancing deployment processes and reducing downtime during rollouts.}
\item {\small Implemented Infrastructure as Code (IaC) using Terraform and AWS CloudFormation to provision and manage cloud resources systematically and efficiently.}
\item {\small Managed continuous integration and continuous deployment (CI/CD) pipelines using Jenkins, GitLab CI, and GitHub Actions, which streamlined software releases and improved code quality.}
\item {\small Utilized Ansible for configuration management across development and production environments, ensuring consistency and automating routine setup tasks.}
\item {\small Monitored and analyzed system performance using Prometheus, Grafana, and AWS CloudWatch, enabling proactive optimizations and rapid troubleshooting.}
\item {\small Employed AWS services such as EC2, S3, and Lambda to enhance the scalability and reliability of applications, reducing operational costs and improving response times.}
\item {\small Developed and maintained robust, secure database solutions using MongoDB and PostgreSQL, optimizing data retrieval and storage strategies to support high-load applications.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Water Potability Analytics} \textit{Next.js, Python, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack water quality assessment tool using Python for backend data processing, MongoDB for data storage, and Next.js for the frontend. Deployed the application on AWS to ensure scalability and high availability.}
\end{itemize}

\noindent \textbf{Pizza Ordering Schema Optimization} \textit{Oracle PL/SQL, Next.js, Node.js, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Engineered a full stack solution for a pizza ordering system, designing the database schema with Oracle PL/SQL and implementing the user interface and server-side logic using Next.js and Node.js. Hosted the application on AWS for robust cloud-based operations.}
\end{itemize}

\noindent \textbf{Sales Insights for Brick \& Mortar Business} \textit{Power BI, SQL, React.js, Node.js, MongoDB} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Crafted a full stack BI tool for sales analysis, utilizing SQL for data management, React.js for dynamic frontend visualization, and Node.js with MongoDB for backend processing. Enhanced decision-making capabilities for business operations.}
\end{itemize}

\noindent \textbf{T20 World Cup Cricket Data Analytics} \textit{Python, Pandas, Next.js, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack cricket team selection tool, using Python and Pandas for data analysis, Next.js for the frontend, and MongoDB for data storage. Deployed on AWS to ensure performance and scalability during high traffic events like the T20 World Cup.}
\end{itemize}

\noindent \textbf{HR Data Analytics} \textit{Power BI, Excel, Next.js, Node.js, MongoDB} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and implemented a full stack HR dashboard using Next.js for the frontend, Node.js and MongoDB for backend operations, and Power BI for advanced data visualization, significantly streamlining HR operations.}
\end{itemize}

\noindent \textbf{Revenue Insights in the Hospitality Domain} \textit{Power BI, Excel, React.js, Node.js, MongoDB, AWS} \hfill \textbf{}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a full stack dashboard to analyze revenue trends, using React.js for the frontend, Node.js for server-side logic, MongoDB for data handling, and AWS for deployment, providing crucial insights to recover revenue and market share.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small 2020: Awarded by Tops Technologies for excellence in Cyber Security}
\item {\small 2020: Recognized in the Discoveri Lite (Industry 4.0) program by SkillAssure}\\
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{Research}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small 2021: Published in the International Research Journal of Engineering and Technology (IRJET), Volume 8, Issue 4, April 2021. Title: "Food Recipes Recommendation System".}
\end{itemize}


\end{document}