\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Nagaraju Dasara \\}
\normalsize \textbf{nagarajudasara@gmail.com $\mid$ +1 (315) 603-7692 $\mid$ Potsdam, NY, USA $\mid$ \href{https://www.linkedin.com/in/nagaraj-yadav/}{LinkedIn} $\mid$ \href{https://github.com}{GitHub} \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Computer Science} \hfill \textbf{2023 - Present} \\
\textit{Clarkson University, Potsdam, NY, USA} \\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}
\end{itemize}
\textbf{Bachelor of Technology in Computer Science and Engineering} \hfill \textbf{2017 - 2021} \\
\textit{Indian Institute of Information Technology, Nagpur, India} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages}{: \small Python, SQL, Java, R, JavaScript, Bash, Scala, HTML, CSS} \\
\textbf{Data Analysis Tools}{: \small Pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch, Excel} \\
\textbf{Business Intelligence Tools}{: \small Tableau, Power BI, Looker, Google Data Studio} \\
\textbf{Data Engineering Tools}{: \small Apache Kafka, Apache Hadoop, Apache Spark, Apache Airflow, Apache Flink, Jenkins, Docker, Kubernetes} \\
\textbf{Databases}{: \small PostgreSQL, MySQL, MongoDB, SQLite, Redis, Elasticsearch, DynamoDB} \\
\textbf{Developer Tools}{: \small Git, Jupyter, RStudio, BitBucket, GitLab, Terraform, Postman} \\
% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Data Engineer | } Click2Cloud Inc., India  \hfill \textbf{October 2021 — August 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed and optimized data ingestion and processing pipelines using RabbitMQ and Kafka for high throughput needs, reducing latency and error rates in data handling by 30\%.}
\item {\small Engineered robust data management solutions with Go and Django, supporting multi-cluster configurations to improve data processing and operational efficiency by 50\%.}
\item {\small Enhanced data integration capabilities for Windows Container support using Docker and Kubernetes, facilitating smoother workflows and increasing platform compatibility.}
\item {\small Implemented Azure Logic Apps for automated data flow visualization, improving compliance tracking and client data handling efficiencies.}
\item {\small Created advanced data simulation tools in Python to predict system behavior, which aided in reducing system downtime and optimizing maintenance schedules.}
\item {\small Automated cloud-based resource deployment using Terraform and PowerShell scripts, which streamlined operations and reduced deployment times by 40\%.}
\item {\small Designed a Python framework for real-time IoT device management, enhancing the integration of data streams into analytics platforms and cloud storage solutions.}
\end{itemize}

\noindent \textbf{Data Analyst Intern | } Mastersoft ERP Pvt Ltd, India \hfill \textbf{August 2020 — February 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Participated in all phases of the software development life cycle, focusing on optimizing client engagement through active feedback integration.}
\item {\small Automated data processing tasks, including CSV generation and manipulation using Python, which streamlined data operations and significantly reduced errors by over 50\%.}\\
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{PROJECT WORK}} \\
\noindent \textbf{Defence Security System (Real Time) | } \textit{Machine Learning, Artificial Intelligence, Python} \hfill \textbf{Dec 2024}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a real-time defense security system using Python. Integrated Machine Learning and Artificial Intelligence to enable automated threat detection, significantly enhancing system responsiveness and operational efficiency.}
\item {\small Applied data analytics to improve algorithm accuracy and system reliability, optimizing response strategies based on predictive modeling and pattern recognition.}
\end{itemize}

\noindent \textbf{Identifying Disease Drug for Drug Repurposing using RWR | } \textit{Python, TensorFlow, Machine Learning} \hfill \textbf{Sep 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Engineered a predictive model using the Random Walk with Restart (RWR) algorithm in Python and TensorFlow to identify potential drug targets, enhancing drug repurposing efforts and reducing development costs.}
\item {\small Utilized advanced data analysis techniques to analyze genetic data and interaction networks, leading to more accurate predictions and insights into disease mechanisms.}
\end{itemize}

\noindent \textbf{Car Parking Reservation System | } \textit{C++, Object-Oriented Programming} \hfill \textbf{Jun 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Built an object-oriented car parking management system in C++, focusing on efficient space allocation and automated billing systems, which streamlined operations and improved user satisfaction.}
\item {\small Implemented data structures to optimize parking lot management and tracking, improving system throughput and minimizing manual intervention.}\\
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS AND CERTIFICATIONS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Finished in the top 10\% in National Science Examination conducted by IAPT in 2015.}
\item {\small Appeared in Final level NTSE and RMO Examinations in 2017.}
\item {\small Achieved 25th DSL rank in Math Scholarship Exam in 2014.}
\item {\small Distinctive participation in the 7th International Mathematics Olympiad in 2013.}
\item {\small Distinctive participation in the 4th International Mathematics Olympiad in 2010.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\end{document}