\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Kabir Singh \\}
\normalsize \textbf{kabsing@clarkson.edu $\mid$ New York, United States $\mid$ (315) 244-8021 $\mid$  \href{https://www.linkedin.com/in/kabir-singh-a862b7235}{Linkedin} \\}
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Bachelor of Science, Double Major in Mechanical Engineering \& Aerospace Engineering} \hfill \textbf{May 2025} \\
\textit{Clarkson University, Potsdam NY, USA} \\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Design \& Simulation Software}{: \small SolidWorks, XFLR5, Altair SimLab, Ansys System Tool Kit, Xfoil, AutoCAD} \\
\textbf{Mechanical Engineering Tools}{: \small 3D Printing, Data Acquisition Systems (Ni Max \& Labview), Machine Shop Certified, CNC Machining} \\
\textbf{Electrical \& Programming}{: \small MATLAB, Simulink, Arduino, Breadboards, Raspberry Pi, PLC Programming} \\
\textbf{Finite Element Analysis}{: \small Altair SimLab (FEA software), Ansys Mechanical} \\
\textbf{Data Analysis \& Programming}{: \small Python, MATLAB, R, SQL, Octave} \\
\textbf{Developer \& Aerodynamics Tools}{: \small Git, Jupyter, RStudio, Visual Studio Code, Computational Fluid Dynamics (CFD), OpenFOAM} \\

% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}}\\
\noindent \textbf{Student Life Assistant, Clarkson University} \hfill \textbf{Aug 2023 – Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Supported the planning and execution of campus-wide events such as orientation and spirit week, enhancing student engagement and fostering a vibrant community atmosphere.}
\item {\small Collaborated in program development to enhance leadership and civic responsibility among students.}
\item {\small Assisted in managing the Student Center and Office of Student Life desks, providing support and information to students and staff.}
\item {\small Contributed to the refinement of student activities, ensuring they meet the diverse needs and interests of the student population.}
\end{itemize}

\noindent \textbf{Peer Educator, Clarkson University} \hfill \textbf{Apr 2022 – Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Facilitated academic and social integration for first-year students by leading sessions that covered essential college transition topics.}
\item {\small Developed and delivered educational content aimed at helping new students build a strong foundation for their college careers.}
\item {\small Acted as a mentor and resource, guiding students through their initial academic and personal challenges at university.}
\end{itemize}

\noindent \textbf{Resident Advisor (HEOP), Clarkson University} \hfill \textbf{Jun 2023 – Jul 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Managed and supported a group of scholars during the SPREE summer pre-freshman program, facilitating their adjustment to college life.}
\item {\small Organized and led various activities that introduced students to key aspects of academic success and campus resources.}
\item {\small Collaborated with other resident advisors and HEOP staff to provide a supportive and educational environment for all participants.}
\item {\small Provided personalized support and guidance to students, helping them to navigate the challenges associated with higher education.}\\
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{PROJECT WORK} \\
\noindent \textbf{Aircraft Structural Analysis, Clarkson University} \hfill \textbf{Ongoing}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Conducted structure and failure analysis for the fuselage of Boeing Vertol CH-46 Sea Knight utilizing MATLAB for computational modeling, Solidworks for 3D modeling, XFLR5 for aerodynamic simulation, and Gantt charts for project management, focusing on optimizing design and enhancing safety measures.}
\item {\small Modeled and analyzed the Fair Child C119 wings and stabilizers in SolidWorks, assessing lift, drag, and pitching moments under various flight conditions with XFLR5 to determine optimal angles of attack for different flight maneuvers, integrating advanced aerospace engineering techniques and analytical methods.}
\end{itemize}

\noindent \textbf{Aircraft Performance and Flight Mechanism, Clarkson University} \hfill \textbf{Ongoing}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Analyzed aircraft performance fundamentals, including propeller and jet dynamics, steady and accelerated flight mechanics, using MATLAB and aerospace simulation software to enhance understanding of flight operations and contribute to design improvements.}
\end{itemize}

\noindent \textbf{Aero Engineering Test and Laboratory, Clarkson University} \hfill \textbf{2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Investigated wing vibration and pressure dynamics, force balance, and structural integrity through comprehensive wind tunnel testing and flow visualization studies on airfoils during the Fall 2023 semester, utilizing advanced testing equipment and analytical software to validate aerodynamic properties and structural designs.}
\item {\small Conducted experiments using electromechanical instruments, circuits, actuators, and controls, integrating data acquisition systems for first-order uncertainty analysis. Empirically aligned results with theoretical engineering principles from material science, statics, strength of materials, rigid body dynamics, and electrical science, demonstrating proficiency in both experimental and theoretical engineering disciplines.}\\
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{LEADERSHIP AND INVOLVEMENT}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small President, South Asian Student Intercultural Association}\item {\small Public Relations Chair, Tau Kappa Epsilon}
\item {\small E-board Member, Studio Manager for Clarkson CCTV Club}
\item {\small Active Member of the Clarkson Union Board, American Institute of Aeronautics and Astronautics, International Student Organization, and Society of Asian Scientists and Engineers.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{AWARDS AND ACHIEVEMENTS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small President's Challenge, Clarkson University, Third place in Human Health, Second place in Prototyping/Designing, First place in Video Creation.}
\end{itemize}



\end{document}