\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Arunima Sharma \\}
\normalsize \textbf{\href{mailto:arunima4work@gmail.com}{arunima4work@gmail.com} $\mid$ +1 647 561 0963 $\mid$ \href{https://www.linkedin.com/in/arunima13}{LinkedIn}} $\mid$ 
\href{https://www.github.com/arunima777} \textbf{Github}}
$\mid$ \normalsize \textbf{Toranto, Canada \\}
\rule{\textwidth}{1pt}
\end{center}

\noindent \textbf{\underline{PROFESSIONAL SUMMARY}} \\
{\small Highly skilled Business Analyst with extensive experience in data intelligence, project management, and Agile methodologies. Proven track record of improving operational efficiency and stakeholder satisfaction across diverse industries.}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science, Project Management} \hfill \textbf{Sept 2021 - Apr 2023} \\
\textit{Northeastern University, Toronto, Canada (GPA: 3.8/4)}  
\end{itemize}
\vspace{1mm}
\textbf{Bachelor of Technology, Engineering} \hfill \textbf{Aug 2005 - Aug 2009} \\
\textit{Satyabhama University, India (GPA: 3.2/4)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Business Analysis Tools}{: \small Microsoft Visio, Lucidchart, Miro, Balsamiq, Atlassian Jira, Rally, Slack, Informatica.} \\
\textbf{Data Intelligence Tools}{: \small Tableau, Power BI, Looker, Google Data Studio, SAS Visual Analytics, Qlik.} \\
\textbf{Programming Languages and Databases}{: \small SQL, Python, SQL, Microsoft SQL Server, MySQL.} \\
\textbf{Project Management Tools}{: \small Microsoft Project, Jira, Trello, Microsoft Office Suite (Excel, Word, PowerPoint), Google Suite, Confluence.} \\
\textbf{CRM \& ERP}{: \small Salesforce, Microsoft Dynamics CRM, SAP, Oracle ERP.} \\
\textbf{Core Competencies}{: \small Team Development, Interpersonal Skills, Customer Relationship Management (CRM), Creative Problem Solving.} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Business Analyst | NEU Finance Portal – Northeastern's Experiential Learning} \hfill \textbf{December 2022 – April 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Utilized Power BI to create comprehensive data visualizations that significantly improved the understanding of payment systems for over 500 students and staff, effectively reducing transaction errors by 20\%.}
\item {\small Managed and optimized Jira workflows to significantly increase team delivery efficiency by 25\%, successfully tracking and reporting on over 150 critical project tasks.}
\item {\small Designed and implemented a CRM strategy with Salesforce that enhanced user engagement and feedback collection, significantly increasing stakeholder satisfaction by 40\% through effective communication.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst | Client Initiative at Northeastern} \hfill \textbf{January 2022 – July 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Spearheaded a business process re-engineering project using Lucidchart to streamline operations across five locations, which successfully increased operational efficiency by 35\%.}
\item {\small Implemented agile using Rally to enhance project transparency and improve the sprint completion rate by 30\% within just six months.}
\item {\small Conducted advanced SQL data analyses to accurately forecast market trends, informing sustainable practices that led to a substantial 15\% increase in client revenue.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Deputy Manager (P\&A) | UBI Tech Pvt. Ltd.} \hfill \textbf{October 2020 – October 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Streamlined performance evaluation processes using Microsoft Office tools, setting clear goals with 100 employees which enhanced individual and team performance by 25\% over the year.}
\item {\small Overhauled day-to-day office operations, including facilities management and procurement processes, which improved operational efficiency by 30\% and reduced overhead costs by 15\%.}
\item {\small Implemented and managed new health and safety policies, ensuring compliance with regulations and reducing workplace incidents by 40\% through effective system enhancements and employee training.}
\end{itemize}

\noindent \textbf{Business Analyst | HCL Technologies, Client: Walmart} \hfill \textbf{June 2016 – November 2019}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed real-time dashboards in Google Data Studio to monitor third-party integrations, enhancing operational oversight and reducing system errors by 25\% effectively.}
\item {\small Leveraged SQL Server to optimize data flows and significantly improve the efficiency of content management systems, achieving a noticeable 20\% increase in process speed.}
\item {\small Facilitated team development and problem-solving sessions that significantly improved project alignment and reduced conflicts by 40\%, enhancing overall project cohesion.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst | Wipro Technologies, Client: Price Chopper - Market 32} \hfill \textbf{Mar 2010 – Jun 2016}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed and managed a POS implementation plan using SAP, which effectively reduced checkout time by 25\% across 50 stores.}
\item {\small Automated report generation in Looker for inventory and sales data, which significantly enhanced decision-making efficiency by 40\%, supporting critical business operations.}
\item {\small Trained and led a team of 10 analysts in Agile and Scrum methodologies, increasing productivity by 20\%, optimizing project outcomes.}
\item {\small Utilized Informatica to manage data integration projects, improving data accuracy and availability by 30\%, critical for making real-time informed business decisions.}
\end{itemize}


\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{CERTIFICATIONS}} 
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Certified Scrum Product Owner (CSPO)}\hfill \textbf{December 2022}
\item {\small Project Management Professional (PMP)}\hfill \textbf{August 2022}
\item {\small Safe 6.0 Scrum Master (SSM)}\hfill \textbf{January 2022}
\item {\small Certified Scrum Master (CSM)}\hfill \textbf{December 2021}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
