%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}

%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}

% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}


% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}


% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }



% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

\begin{flushleft}
    \textbf{\large Ishan Joshi} \\    
    \textit{Baltimore, United States} $|$ 
    \textit{+1 (551) 344-7885‬} $|$  
    \href{mailto:ishan.joshiapplication@gmail.com}{{\textit{Email}}} $|$ 
    \href{https://www.linkedin.com/in/ishanjoshi6286/}{{\textit{linkedin}}} $|$
    \href{https://123ishan.github.io/portfolio/}{{\textit{github}}}
    \vspace{-8pt}
\end{flushleft}

% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------

\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     {Experiance software developer with 5+ years expertise in full-stack development and Devops, delivering well-documented and tested solutions. Demonstrates strong collaborative skills and a proven ability to communicate and innovate independently.} \\      
    }}
 \end{itemize}
 \sectionspace


% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

% \section{Awards and Certifications}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\titleItem{Star Award} \emph{ $|$ Company 1}}{September 2018}
%       \resumeProjectHeading
%           {\titleItem{Kudos Award} \emph{ $|$ Company 2}}{May 2017}
%       \resumeProjectHeading
%           {\titleItem{IBM Full Stack Software Developer} \emph{$|$ IBM}}{November 2023}
%           \resumeProjectHeading
%           {\titleItem{CompTia Sec+} \emph{$|$ CompTia}}{December 2023}
%     \resumeSubHeadingListEnd
% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------
\section{Technical Skills}
\subheadingtitlevspace
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \titleItem{Programming Languages}{: Java, Python, JavaScript, SQL, Bash Scripting} \\
     \titleItem{Frameworks \& Libraries}{: Spring Boot, Spring MVC, Hibernate, React JS, Angular JS, Node.js} \\
     \titleItem{DevOps Tools \& Clouds}{: Docker, Kubernetes, Jenkins, Git, Azure DevOps, Ansible, Terraform, AWS, Google Cloud Platform} \\
     \titleItem{Database Management}{: MySQL, MongoDB, Oracle DBMS, PostgreSQL} \\
     \titleItem{Monitoring Tools}{: Prometheus, Grafana, ELK Stack (Elasticsearch, Logstash, Kibana)} \\
     \titleItem{Additional Skills}{: REST API, JSON, Microservices Architecture, Data Modelling, Agile Methodologies (Scrum/Kanban), Continuous Integration/Continuous Deployment (CI/CD)}
    }}
\end{itemize}
\sectionspace




    
% -------------------------------------
%----------EXPERIENCE------------------
% -------------------------------------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
         {\textbf{Data Analyst} $|$ \emph{Holland America Group}, Seattle, WA}{May 2023 - Spetember 2023}
    \resumeItemListStart
      \resumeItem{Analyzed and interpreted complex data sets using SQL and Python, identifying key trends that influenced strategic decisions and resulted in a 15\% increase in operational efficiency. Utilized advanced data analytics, machine learning models, and visualization tools.}
      \resumeItem{Managed and optimized large-scale data processes involving over 2 TB of data, employing techniques in data cleaning, manipulation, and extraction to enhance marketing strategies.}
      \resumeItem{Conducted multi-dimensional data analysis integrating SQL, Python, and Tableau for comprehensive business intelligence and customer insights, significantly boosting sales metrics.}
      \resumeItem{Developed predictive models and automated data pipelines using SQL, Python, and R, enhancing business decision-making processes and operational responsiveness.}
    \resumeItemListEnd

    \resumeProjectHeading
         {\textbf{Senior Software Development Engineer} $|$ \emph{Volkswagen Group IT Services}, India}{September 2019 -- September 2022}
    \resumeItemListStart
      \resumeItem{Architected and deployed scalable microservices using Java and Spring Boot, incorporating Docker and Kubernetes for container management and orchestration, leading to improved system resilience and efficiency.}
      \resumeItem{Led the front-end and back-end development of an SLA Tracker using React.js, Node.js, and integrating RESTful APIs, achieving project goals under budget and enhancing service reliability.}
      \resumeItem{Supervised a cross-functional development team employing Agile methodologies and continuous integration/continuous deployment (CI/CD) practices to speed up delivery and enhance product quality.}
      \resumeItem{Optimized front-end performance by implementing state management solutions in React, improving user engagement and operational efficiency through enhanced UI/UX designs.}
    \resumeItemListEnd

    \resumeProjectHeading
         {\textbf{Web Development Intern} $|$ \emph{Spring Jaunter}, India}{January 2019 -- March 2019}
    \resumeItemListStart
      \resumeItem{Engineered and deployed a full-stack solution using React.js and Node.js, focusing on streamlining operational processes through automated solutions and advanced web technologies.}
      \resumeItem{Contributed to a major e-commerce platform overhaul, improving system architecture and enhancing front-end features using HTML5, CSS3, and JavaScript to elevate user experience and conversion rates.}
      \resumeItem{Developed custom internal applications focusing on productivity improvements, employing modern JavaScript frameworks and server-side technologies to automate routine tasks effectively.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------

% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {University of Utah}{Salt Lake City, UT}
%       {MS in Computer Science | GPA: 3.86}{January 2021 -- December 2023} 
%     \resumeSubheading
%       {SRM University}{Chennai, TN, India}
%       {Bachelor of Technology in Computer Science and Engineering | GPA: 3.4}{August 2012 -- May 2016}
%   \resumeSubHeadingListEnd
% \vspace{-12pt}

\section{Education}    
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\titleItem{{Master Of Science In Information Systems}} $|$ \emph{3.7}}{August 2022 -- May 2024}
           \resumeItem{{University of Maryland} $,$ \emph{Baltimore, MD, USA}}
       \resumeProjectHeading
           {\titleItem{{Bachelor of Engineering in Computer Science}} $|$ \emph{3.9}}{July 2015 -- May 2019}
           \resumeItem{{Pune University} $,$ \emph{Pune, India}}
     \resumeSubHeadingListEnd

% -------------------------------------
%----------PROJECTS--------------------
% -------------------------------------

 \section{Projects}    
     \resumeSubHeadingListStart
        \resumeProjectHeading
           {\textbf{Automatic Diagnosis of Quantum Software Bug-Fix} $|$ \emph{Python, Algorithm Development, System Debugging}}{\href{https://tinyurl.com/GITQUNTUM}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Engineered an automated diagnostic system for quantum software bugs, utilizing advanced algorithms to reduce bug resolution time by 50\%. Demonstrated proficiency in Python, algorithm optimization, and system debugging.}
           \resumeItemListEnd
       
        \resumeProjectHeading
           {\textbf{Water Potability Analysis} $|$ \emph{Data Science, Python, Jupyter}}{\href{https://github.com/123Ishan/Water-Potability}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Leveraged Python in a Jupyter notebook environment to analyze and visualize water quality data, applying data science techniques to ensure health and safety compliance. Skills in data manipulation and statistical analysis were critical.}
           \resumeItemListEnd
           
        \resumeProjectHeading
           {\textbf{Deep Learning Model for Diabetic Retinopathy} $|$ \emph{Machine Learning, Python, Image Processing}}{\href{https://github.com/123Ishan/Diabatic-Retenipathy-Detection}{{\textit{Github}}}}
            \resumeItemListStart
            \resumeItem{Employed Python and advanced image preprocessing techniques; evaluated models using metrics like accuracy, precision, recall, IoU, and Dice Coefficient, focusing on machine learning and performance optimization.}
           \resumeItemListEnd

        \resumeProjectHeading
           {\textbf{Android Application for Road Smoothness} $|$ \emph{Full-Stack Development, Java, JSP, GPS Integration}}{}
            \resumeItemListStart
            \resumeItem{Utilized Java Server Pages (JSP), HTML, CSS with Bootstrap for the app's backend and frontend development. Integrated GPS data handling and real-time alert mechanisms, demonstrating skills in full-stack development and user interface design.}
           \resumeItemListEnd
     \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
