\documentclass{article}

\usepackage[top=0.3in, bottom=0.2in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Siddharth Malav \\}
\normalsize \textbf{Los Angeles, CA, USA } $\mid$ +1 9517423532 $\mid$ \href{http://www.linkedin.com/in/siddharth-malav}{LinkedIn}
\rule{\textwidth}{1pt}
\end{center}


\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Business Administration} \hfill \textbf{August 2022 – May 2024} \\
\textit{University of California , Riverside, CA, USA (GPA: 3.53/4)}  
\end{itemize}
\vspace{2mm}
\textbf{Bachelor of Computer Application Concentration- Game development} \hfill \textbf{August 2016 – May 2020} \\
\textit{CMR University , Bengaluru, India }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\noindent \textbf{Data Analysis and Visualization:} \small Microsoft Power BI, Tableau, SQL, R, Excel (advanced) \\
\noindent \textbf{Business Analysis Tools:} \small Advanced Excel, MS Visio, Lucidchart, Microsoft Project, Balsamiq, SWOT Analysis \\
\noindent \textbf{Project Management:} \small Agile methodologies, Scrum, Kanban, JIRA, Trello, Microsoft Project, Confluence \\
\noindent \textbf{Process Improvement:} \small Lean, Six Sigma, BPMN (Business Process Model and Notation), Kaizen \\
\noindent \textbf{Communication:} \small Stakeholder management, requirements gathering, workshop facilitation, business writing, presentation skills \\
\noindent \textbf{Technical Proficiencies:} \small Python, Java, API development, Docker, Kubernetes, SQL, UML (Unified Modeling Language)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent \textbf{Business Analyst $\mid$ NEU Finance Portal $\mid$ Northeastern's Experiential Learning} \hfill \textbf{March 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Created detailed Power BI visualizations that significantly improved the understanding of complex payment systems for over 500 students and staff, reducing transaction errors by 20\% through actionable data-driven insights.}
\item {\small Managed and optimized Jira workflows, which resulted in a 25\% increase in team delivery efficiency, successfully tracking and reporting on over 150 critical project tasks using Agile and Scrum methodologies.}
\item {\small Designed and implemented a comprehensive CRM strategy with Salesforce, enhancing user engagement and feedback collection processes, significantly boosting stakeholder satisfaction by 40\% through effective communication channels.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst $\mid$ Client Initiative at Northeastern} \hfill \textbf{October 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Led a business process re-engineering project utilizing Lucidchart, successfully streamlining operations across five locations and increasing operational efficiency by 35\% through detailed and accurate process mapping.}
\item {\small Implemented Agile methodologies using Rally, which improved project transparency and increased the sprint completion rate by 30\% within six months through iterative development and effective backlog management.}
\item {\small Conducted advanced SQL data analyses to accurately forecast market trends, leading to a substantial 15\% increase in client revenue through the use of predictive analytics and detailed trend analysis.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Deputy Manager (P\&A) $\mid$ UBI Tech Pvt. Ltd.} \hfill \textbf{October 2023 – December 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Streamlined performance evaluations using advanced Microsoft Office tools, setting clear and measurable KPIs for 100 employees, which enhanced individual and team performance by 25\% through goal alignment and consistent feedback.}
\item {\small Overhauled day-to-day office operations, improving overall efficiency by 30\% and reducing overhead costs by 15\% through strategic process optimization and effective procurement management techniques.}
\item {\small Implemented new health and safety policies, ensuring compliance with industry regulations and reducing workplace incidents by 40\% through system enhancements and comprehensive employee training programs.}
\end{itemize}

\noindent \textbf{Business Analyst $\mid$ HCL Technologies, Client: Walmart} \hfill \textbf{June 2020 – August 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Designed and deployed real-time dashboards in Google Data Studio, which improved operational oversight and reduced system errors by 25\% through enhanced data visualization and continuous monitoring.}
\item {\small Optimized data flows and processes with SQL Server, significantly increasing the efficiency of the content management system by 20\% through comprehensive database optimization and streamlined query execution.}
\item {\small Facilitated team development and problem-solving sessions, improving project alignment and reducing conflicts by 40\% through collaborative problem-solving techniques and effective communication strategies.}
\end{itemize}
\vspace{1mm}

\noindent \textbf{Business Analyst $\mid$ Wipro Technologies, Client: Price Chopper - Market 32} \hfill \textbf{December 2019 – November 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed a comprehensive POS implementation plan using SAP, effectively reducing checkout time by 25\% across 50 stores through efficient system integration and process automation.}
\item {\small Automated report generation processes in Looker, significantly enhancing decision-making efficiency by 40\% through the use of improved data analytics and real-time reporting for inventory and sales data.}
\item {\small Trained and led a team of 10 analysts in Agile and Scrum methodologies, increasing overall productivity by 20\% through iterative project management, continuous improvement, and effective team collaboration.}
\item {\small Managed large-scale data integration projects with Informatica, improving data accuracy and availability by 30\% through robust ETL processes and comprehensive data validation techniques.}
\end{itemize}

\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\textbf{Strategic Game Monetization Analysis} $\mid$ \textbf{Python, SQL, R, Tableau}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Led a project to analyze and optimize monetization strategies for a mobile RPG game, utilizing advanced data analytics techniques with Python and SQL, increasing revenue streams by 25\% without compromising user experience.}
\item {\small Conducted A/B testing and data-driven analysis using R and Tableau to determine optimal pricing and in-game purchasing options, resulting in a 20\% increase in user spending and a 15\% improvement in retention rates.}
\end{itemize}
\vspace{2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{AWARDS AND CERTIfiCATIONS}} \\
\noindent \textbf{Digital Product Manager: Modern Fundamentals} $\mid$ University of Virginia  \hfill \textbf{June 2022}\\
\noindent \textbf{Introduction to AWS Identity and Access Management} $\mid$ Amazon Web Services \hfill \textbf{October 2023}\\
\noindent \textbf{Introduction to Identity and Access Management} $\mid$ OKTA \hfill \textbf{November 2023}
\end{document}
