\documentclass{article}

\usepackage[top=0.3in, bottom=0.4in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{Pruthviraj Prakash \\}
\normalsize \textbf{\href{mailto:pruthviraj.prakash32@gmail.com}{pruthviraj.prakash32@gmail.com} $\mid$ +1 (315)-603-7775 $\mid$ \href{https://linkedin.com/in/pruthviraj-p66}{Linkedin} $\mid$ \href{https://github.com/pruthviraj32}{GitHub} \\}
\rule{\textwidth}{1pt}
\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OBJECTIVE
% Who you are, what domain, what are you looking for, and when?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS: Important and relevant to the job you are applying for
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
% University name, degree, year of graduation, GPA (optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{EDUCATION}} \\
\textbf{Master of Science in Computer Science} \hfill \textbf{August 2023 - Present} \\
\textit{Clarkson University, Potsdam, NY}\\
\end{itemize}
\end{itemize}
\textbf{Bachelor of Technology in Electrical and Computer Engineering} \hfill \textbf{August 2016 - March 2020} \\
\textit{PES University, Bangalore, India} \\
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
% What did you do? -> Project goals OR what problem did you solve?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
% Example: 
% + Developed an app for matching mentors and mentees for Android and iOS platforms.
% + Successfully matched 85% of the applications and randomized the rest.
% 
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages}{: \small Data Structures, Algorithms, C, C++, Java, Python, Kotlin} \\
\textbf{Backend Development}{: \small Spring Framework, Hibernate, Microservices, FastAPI, Java Persistence API, JSON Web Tokens, REST API} \\
\textbf{DevOps Tools \& Cloud}{: \small Docker, Kubernetes, Jenkins, Terraform, Git, AWS (EC2, S3, RDS, Lambda), Google Cloud Platform} \\
\textbf{Monitoring and Logging}{: \small Prometheus, Grafana, ELK Stack (Elasticsearch, Logstash, Kibana), Splunk} \\
\textbf{Databases}{: \small MySQL, PostgreSQL, MongoDB, Oracle Database, Redis} \\
\textbf{API Development}{: \small REST, GraphQL, Swagger, Postman} \\
\textbf{Machine Learning}{: \small TensorFlow, Keras, Scikit-learn, pandas, PyTorch} \\


% Skill 1 (level of expertise), Skill 2 (level of expertise), Skill 3 (level of expertise) \\

\noindent \textbf{\underline{WORK EXPERIENCE}}\\
\noindent \textbf{Machine Learning Engineer (RA) | Clarkson University} \hfill \textbf{September 2023 - Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Expertly leveraged Python and OpenCV on NVIDIA Jetson Orin for real-time face and iris recognition, focusing on optimizing and refining algorithms for improved long-range identification accuracy and reliability.}
\item {\small Meticulously engineered and fine-tuned robust feature identification algorithms for the PTZ camera system, significantly enhancing the system's recognition performance and operational efficacy at distances of up to 5 meters.}
\item {\small Applied advanced machine learning models to analyze and process biometric data, achieving a high degree of precision in challenging lighting and movement conditions.}
\end{itemize}
\noindent \textbf{SDET Engineer | Enquero (Genpact), India} \hfill \textbf{August 2021 - May 2023}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed and maintained automated testing scripts, enhancing test efficiency by 40\% and reducing manual testing efforts by 30\%.}
\item {\small Configured and managed Jenkins pipelines for continuous integration and deployment, improving code deployment frequency by 25\% and reducing release problems.}
\item {\small Employed both manual and automated testing techniques, ensuring all-round quality assurance which decreased defect rates by 20\% across various project phases.}
\item {\small Authored robust automated testing scripts, which decreased testing time by 50\% and improved test repeatability and accuracy.}
\end{itemize}
\noindent \textbf{Software Engineer | Enquero (Genpact), India} \hfill \textbf{August 2020 - May 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Analyzed historical data and predicted future trends using SQL and Python for the Hasbro P\&L project, leading to a 10\% increase in forecast accuracy.}
\item {\small Utilized Azure cloud services and Databricks for data processing, enhancing project scalability and data processing speed by 30\%.}
\item {\small Crafted and optimized complex SQL queries for data transformation, improving data analysis efficiency for strategic decision-making.}
\item {\small Developed Tableau dashboards for data visualization that helped stakeholders visualize profit and loss trends, increasing business decision speed by 15\%.}
\end{itemize}
\noindent \textbf{Software Developer Intern | Enquero (Genpact), India} \hfill \textbf{December 2019 - May 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Completed a comprehensive training program in software development using Python, C, C++, Java, and JavaScript, gaining proficiency in multiple programming languages.}
\item {\small Developed 'Skill Matrix,' a full-stack web application using Java, Nextjs, effectively managing skills data for 300+ employees.}
\item {\small Managed a large dataset integration for the 'Skill Matrix' application, enhancing project alignment and efficiency in employee project assignments.}
\end{itemize}
\noindent \textbf{Intern | Microsoft Innovation Lab, PES University, India} \hfill \textbf{May 2018 - July 2018}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed and integrated software components for a Smart Lamp Post project using Python and Arduino-C++, which improved system functionality and user interaction.}
\item {\small Performed extensive research and implementation of emerging tech, significantly enhancing project innovation and technology adoption.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT
% What did you do?
% How did you do it? -> Skills and technologies
% What impact did you create? -> Numbers and percentages.
%
% Talk about teamwork, initiative, and soft skills.
%
% Can also include personal projects, competitions, and contributions to Open source.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\noindent \textbf{\underline{PROJECT WORK}} 

\noindent \textbf{Fine Grained Statistical Debugging for the Identification of Multiple Bugs}
\textit{\href{https://www.ijert.org/fine-grained-statistical-debugging-for-the-identification-of-multiple-bugs}{Link}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Implemented statistical analysis techniques for software bug detection, significantly reducing error rates and improving system dependability.}
\item {\small Contributed to a peer-reviewed journal paper, detailing innovative debugging methods and their impact on software quality assurance.}\\
\end{itemize}
\noindent \textbf{Drowsiness Detection Using Image Processing with GSM}
\textit{\href{https://www.irjet.net/archives/V8/i5/IRJET-V8I5773.pdf}{Link}}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item {\small Developed an image processing-based drowsiness detection system, using machine learning to minimize accidents from driver fatigue.}
\item {\small Integrated GSM module for immediate alert transmission, enhancing driver safety by prompt identification of fatigue indicators.}\\
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Extra Curricular Activities, Leadership, etc 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Skills: you can add all your other skills here.
% Continue to keep only relevant skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}