\documentclass{article}

\usepackage[top=0.2in, bottom=0.2in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref} % Include the hyperref package


\usepackage{hyperref}

\begin{document}
\begin{center}
\thispagestyle{empty}
\large \textbf{\textbf{Naman Mittal}  \\}
\normalsize apt 307, Lake Mary, Florida $\mid$ (951) 557-4947 $\mid$ \href{mailto:nmitt005@ucr.edu}{Email} $\mid$ \href{www.linkedin.com/in/nmittal99}{LinkedIn} $\mid$  \href{github.com/palindrome1311}{Github} $\mid$  \href{www.mittalnaman.com}{Website}  \\
\rule{\textwidth}{1pt}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{EDUCATION}} \\
\noindent \textbf{University of California at Riverside} \hfill \textbf{September 2021 – December 2022} \\
Masters of Science (MS) in Computer Science [3.7/4 GPA]\\\\
\noindent \textbf{Medi-Caps University} \hfill \textbf{August 2017 – May 2021} \\
Bachelors of Technology (B. Tech) in Computer Science [8.3/10 GPA]


\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TECHNICAL PROFICIENCY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{TECHNICAL PROFICIENCY}} \\
\textbf{Languages:} Python, C, C++, Java, JavaScript, TypeScript, PHP, HTML, CSS, XML, R\\
\textbf{Databases}{ SQL, MySQL, PostgreSQL, MongoDB, Oracle, Cassandra, Data Warehousing, Data Pipeline} \\
\textbf{Frameworks:} Angular, Ionic, React, Node.js, Flask, Django, Material-UI, Bootstrap, Spring, Spring Boot, Next.js, Vue.js\\
\textbf{Libraries:} Docker, Google Cloud Platform (GCP), Amazon Web Services (AWS), TensorFlow, PyTorch, Pandas, NumPy, OpenCV\\
\textbf{Tools:} Git, GitHub, GitLab CI/CD, Jenkins, VS Code, Visual Studio, PyCharm, JaCoCo, Webpack, Babel, Postman, Swagger, Jest, Mocha, Cypress, Enzyme

\vspace{2mm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent \textbf{\underline{WORK EXPERIENCE}} \\
\noindent {\textbf{Full-Stack Software Engineer $\mid$ BNY Mellon}} \hfill \textbf{Febuary 2023 – Present}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed an Angular 14 application for the client-facing Credit Line Monitoring system, reducing page load times by 40\% and improving user engagement by 25\% using Angular, TypeScript, RESTful Services, and Webpack.
\item Designed and implemented unit test cases for 100+ components using Jest and Cypress, achieving 95\% code coverage and reducing bugs by 30\%, leveraging skills in Jest, Cypress, and TypeScript.
\item Built a robust application handling transactions worth trillions regularly, ensuring 99.99\% uptime and improving transaction processing speed by 20\%, utilizing skills in Redux, Git, Responsive Web Design, and Cross-Browser Compatibility.
\end{itemize}

\vspace{1mm}

\noindent {\textbf{Software Engineering Intern $\mid$ loanDepot.com LLC}} \hfill \textbf{June 2022 – August 2022}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed a web service to request payoff and notify customers of quotes via text, .NET Core 3+, and .NET Framework 7.2+, which increased the demand for quotes by 80\%. Utilized skills in Angular 11, .NET Core, .NET Framework, RESTful Services.
\item Designed a customer support chat with a live chat agent feature using Microsoft 365 Dynamics, improving customer service by reducing wait times by 70\%. Leveraged skills in Microsoft 365 Dynamics, JavaScript, and real-time communication protocols.
\item Reduced latency and optimized web application performance by 45\% using Dynatrace by monitoring and analyzing performance using 20+ metrics. Applied skills in Dynatrace, performance tuning, and analytics.
\end{itemize}


\vspace{1mm}

\noindent {\textbf{Machine Learning Intern $\mid$ 3-2-1-GoCheck}} \hfill \textbf{June 2020 – June 2021}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed an OCR system with Python, pytesseract, and TensorFlow YOLOv3, achieving 98\% accuracy in custom object and face detection. Skills used: Python, pytesseract, TensorFlow, machine learning.
\item Improved the entire CI/CD process by integrating Clubhouse with Git repositories, reducing manual updates of user stories by 90\%. Applied skills in CI/CD, Clubhouse, Git, and automation.
\item Programmed a document automation system using Angular 7, eliminating 100\% of human intervention in verifying and updating documents. Leveraged skills in Angular 7, TypeScript, and automation.
\end{itemize}

\vspace{1mm}

\noindent {\textbf{Software Engineering Intern $\mid$ Pryzm IT Solutions}} \hfill \textbf{May 2020 – July 2020}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Converted 50+ UI wireframes into fully functional webpages using HTML, CSS, JavaScript, Bootstrap, and React, increasing user engagement by 20\% and generating \$10,000 in revenue by creating a more visually appealing and user-friendly interface.
\item Implemented over 20 REST microservices for CRUD operations using Java Spring and Spring Boot, reducing server response times by 30\% and enhancing backend efficiency by 25\%, leading to faster data retrieval and processing.
\item Developed a comprehensive dashboard for the Admin Web Portal using Angular 7 and Material UI, improving data visualization and management for 2 million users worldwide and reducing admin processing time by 40\%, enabling data handling.
\end{itemize}

\vspace{1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECT WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{\underline{PROJECTS}} \\
\textbf{Musical Notes Generation using LSTM Neural Networks $\mid$ TensorFlow, Python, Kaggle}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed a Musical Notes Generator with an impressive 88\% accuracy using Python, TensorFlow, and LSTM Neural Networks, capable of producing melodies for a wide range of musical instruments.
\item Significantly reduced training time by 70\% by leveraging high GPU performance on Kaggle Notebooks, which optimized computational efficiency and accelerated the model development process.
\end{itemize}
\vspace{1mm}

\noindent \textbf{Sentiment Analysis on News Headlines and Descriptions $\mid$ Python, Selenium, Flask, NLP}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Created a sentiment analyzer predicting stock movements with 85\% accuracy, analyzing 50,000+ news headlines. Skills: Python, NLP, machine learning.
\item Scraped data from 100+ websites using Python and Selenium, integrating it into a Flask web application for real-time analysis, reducing data processing time by 40\%. Skills: Python, Selenium, Flask, web scraping.
\end{itemize}
\vspace{1mm}

\noindent \textbf{E-Commerce Replica $\mid$ Java, Spring Boot, PostgreSQL, and AWS}
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item Developed a scalable e-commerce application using Java, Spring Boot, JSP, PostgreSQL, and AWS, supporting over 10,000 daily transactions and ensuring seamless user experience.
\item Ensured optimal performance with advanced concurrency handling and load balancing using React, improving user response times by 50\% and maintaining 99.9\% uptime even under high traffic conditions.
\end{itemize}

































\end{document}